---
title: "Unidimensionality and Reliability of DAACS SRL scales; Parallel Analysis, 
EFA, and Alpha/Omega test. WGU. Last Attempt"
author: "Oxana Rosca"
date: "2022-08-06"
output:
  word_document: default
  html_document: default
---
Dataset (N=6648): From the WGU dataset, I removed 211 cases of students who took
more than 1 attempt, so that only the last attempts remained in the dataset.

Result: The total set of all SRL items is expectedly not unidimensional,as well 
as the Motivation scale. However, the Metacognition scale and all sub-scales are 
unidimensional (with a 4:1 or greater ratio for the first and the second 
eigenvalues). Parallel analysis suggested that 6 scales (Metacognition, Anxiety 
Management, Grit-Consistency, Mindset, Help Seeking, and Managing Environment) 
loaded on a single factor each. 
Three scales (Mastery Orientation, On-line Self-efficacy, and Grit Persistency) 
loaded on a single factor.
The Metacognition Scale and 11 subscales (exept ofGritP and Minset) are 
perfectly unidimensional (with an 8:1 or greater ratio).
However, for all subscales, alpha is always greater than omega, which suggests 
that the sets meet alpha's assumptions.  

The literature says that alpha underestimates internal consistency when the set 
does not meet the alpha assumptions, while Omega provides correct estimation for 
multidimensional sets, with correlation between the error terms, 
non-tau-equivalent,and not univariate distributions (which are all assumptions 
of alpha). 

Next step: testing for those assumptions.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library}
library(psych) 
library(psychTools)
library(haven)
library(GPArotation)
```

```{r readin}
daacsSRL <- read_sav("srl.items.score.LastAttempt.wgu_6648.sav")
```

```{r subset}
daacsSRL<-daacsSRL[,c(3:59)]
```

```{r headtail}
headTail(daacsSRL)
```

```{r describe}
describe(daacsSRL)
```
How many variables are in the set
```{r varNumb}
dim(daacsSRL)
```

```{r lowerCor}
lowerCor(daacsSRL)
```

Create a set of scoring keys to tell us which items go on which scales.
The first way of creating keys ( you can use minus sign to reverce-code your items (e.g., TA = c("anxious","jittery","nervous","-calm"):
```{r keys1}
SRL.keys <- list(MoMa= c("MoMa1","MoMa2","MoMa3", "MoMa4","MoMa5", "MoMa6", 
                         "MoMa6"), 
                 MoMo = c("MoMo1","MoMo2","MoMo3", "MoMo4"), 
                 MoMs = c("MoMs1", "MoMs2", "MoMs3", "MoMs4", "MoMs5", "MoMs6"), 
                 SeOL = c("SeOL1", "SeOL2", "SeOL3", "SeOL4"),
                 McE= c("McE1","McE2","McE3", "McE4"), 
                 McM= c("McM1","McM2","McM3", "McM4","McM5", "McM6"), 
                 McP = c("McP1", "McP2", "McP3", "McP4"), 
                 LsHs = c("LsHs1","LsHs2", "LsHs3"), 
                 LsU = c("LsU1", "LsU2", "LsU3","LsU4"), 
                 LsMe = c("LsMe1", "LsMe2", "LsMe3"),
                 LsTm = c("LsTm1", "LsTm2", "LsTm3"),
                 GritP = c("GritPersist1", "GritPersist2", "GritPersist3", 
                           "GritPersist4"), 
                 GritC = c("GritConsist1", "GritConsist2", "GritConsist3", 
                           "GritConsist4", "GritConsist5", "GritConsist6")) 
```
Another way to create the same scoring keys list (with each scale 
loading on a single factor of the same name. Not finished. Use Using R to score 
personality scales_Revelle 2022, p. 10: Creating the second scoring keys list 
with three scales (Metacognition, Anxiety, and Grit Consistency) loading on a 
single factor McMoMa:
```{r keys2}
SRL.keys1 <- list(MoMa= c(1:6), MoMo = c(7:10), MoMs = c(11:16),SeOL = c(17:20),
                 McE= c( 21:24),McM= c(25:30), McP = c(31:34), LsHs = c(35:37), 
                 LsU = c(38:41),LsMe = c(42:44),LsTm = c(45:47), 
                 GritP = c(48:51), GritC = c(52:57))
```

Some people like to find coefficient alpha as an estimate of reliability. This 
is of little use but may be done for a single scale using the alpha function. 
The following analysis presents alpha and omega coefficients. The results 
suggest that the SRL scale has a general factor but it is not unidimentional: 
The degrees of freedom for just the general factor are 1539,and the fit is 14.4; 
the number of observations was  6648  with Chi Square =  95449.15  with 
prob <  0; the df corrected root mean square of the residuals is  0.13; 
the RMSEA index =  0.096  and the 10 % confidence intervals are  0.095 0.096

Step One: Check for Unidimensionality. Strictly speaking, uncorrelated 
factors do not "seriously" affect the alpha when the factors are not correlated; 
But for a multidimensional scale with correlated factors, alpha shows the lower 
bound of reliability. Cronbach himself stated that there is no need for all 
items to be "factorially similar" but a large proportion of the covariation 
among the items has to be due to a general factor(1951, in Bandalos, 2018).
Hence, Bandalos suggests "Strictly speaking, tests for tau-equivalence and 
parallelism should be based on a unidimensional model" p.393.

```{r parallel}
fa.parallel(daacsSRL, fm="pa", fa="fa", main="Total SRL Scale Parallel 
            Analysis", n.iter=1000, SMC=TRUE, show.legend=TRUE)
```

Prallel Analysis suggests 6 factors. 
```{r cfa6SRL}
FA_daacsSRL6f <- fa(daacsSRL, nfactors=6, rotate="oblimin", SMC=TRUE, 
                  max.iter=1000,fm="ml", alpha=.05)
print(FA_daacsSRL6f, sort=TRUE)
```

***Result***
Model fit for 6 factors is good: RMSR = 0.053 and RMSEA 95%CI = [0.052, 0.053],
but McP2, LSU1, LSU2, LSTm1, LSTm2, LsMe1,LsMe2, MoMo1 and GritPersist1-4 have 
low loadings (<0.4) and high commonalities (>1.5). 
Six pairs of factors out of 15 correlate with each other at 0.31-048: Therefore, 
the unidimensionality request of alpha coefficient is not met for the total SRL 
set.

```{r cfa3SRL}
FA_daacsSRL3f <- fa(daacsSRL, nfactors=5, rotate="oblimin", SMC=TRUE, 
                  max.iter=1000,fm="ml", alpha=.05)
print(FA_daacsSRL3f, sort=TRUE)
```

```{r cfa1SRL}
EFA1SRL <- fa(daacsSRL, nfactors=1, rotate="oblimin", SMC=TRUE, max.iter=1000,
fm="pa", alpha=.05)
print(EFA1SRL, sort=TRUE)
```
***Result***
One general factor model has a poor fit: RMSEA 95 % CI = [0.093 0.095], which 
confirms that the total SRL scale is not unidimensional. However, it has a 
strong general factor: 48 out of 57 items have loadings of 0.4 or higher; hense,
the assumption for Omega coefficient is met. 

McDonald has proposed coefficient omega (hierarchical) (ωh) as an estimate of 
the general factor saturation of a test. It is based upon the correlation of 
lower order factors. Zinbarg et al. (2005) and Revelle and Zinbarg (2009) 
compare  McDonald’s ωh to Cronbach’s α and Revelle’s β. They conclude that ωh 
is the best estimate. (See also Zinbarg et al. (2006) and Revelle and Zinbarg 
(2009).

An examination of general factor loadings "constitutes an informal test of the 
omega coefficient assumption that there is a latent variable common to all of 
the scale’s indicators that can be conducted even in the context of EFA. If the 
loadings were salient for only a relatively small subset of the indicators, this 
would suggest that there is no true general factor underlying the covariance 
matrix. Just such an informal assumption test would have afforded a great deal 
of protection against the possibility of misinterpreting the misleading ωh 
estimates occasionally produced in the simulations reported here.”(Zinbarg et 
al., 2006, p 137).

The most critical of the three assumptions is unidimensionality. To test it, we 
use exploratory FA and compare Alpha to measures such as Hierarchical (ωh) and 
Total (ωt) Omegas. These may be found using one of two functions: 
1) the omega function for an exploratory analysis or 
2) omegaSem for a confirmatory analysis using the sem package solution based 
upon the exploratory solution from omega.

The default omega() does a minimum residual factor analysis, fm=“pa” does a 
principal axes factor analysis (factor.pa), and fm=“mle”provides a maximum 
likelihood solution.
If flip =TRUE (the default), items will be reversed so that they have positive 
loadings on the general factor. The keys are reported so that scores can be 
found using the score.items function. Arbitrarily reversing items this way can 
overestimate the general factor.

ωt is an estimate of the total reliability of a test.

```{r}
daacsMetacog<-daacsSRL[,c(21:34)]
head(daacsMetacog)
fa.parallel(daacsMetacog, fm="pa", fa="fa", main="Metacognition Scale", 
            n.iter=1000, SMC=TRUE, show.legend=TRUE)
```

```{r}
daacsEval<-daacsSRL[,c(21:24)]
head(daacsEval)
fa.parallel(daacsEval, fm="pa", fa="fa", main="Evaluation Subscale", 
            n.iter=1000, SMC=TRUE, show.legend=TRUE)
```

```{r}
daacsMonit<-daacsSRL[,c(25:30)]
head(daacsMonit)
fa.parallel(daacsMonit, fm="pa", fa="fa", main="Monitoring Subscale", 
            n.iter=1000, SMC=TRUE, show.legend=TRUE)
```

```{r}
daacsPlan<-daacsSRL[,c(31:34)]
head(daacsPlan)
fa.parallel(daacsPlan, fm="pa", fa="fa", main="Planning Subscale", 
            n.iter=1000, SMC=TRUE, show.legend=TRUE)
```

```{r}
daacsMotiv<-daacsSRL[,c(1:20, 48:57)]
head(daacsMotiv)
fa.parallel(daacsMotiv, fm="pa", fa="fa", main="Motivation Scale", 
            n.iter=1000, SMC=TRUE, show.legend=TRUE)
```

```{r}
daacsAnxietyM<-daacsSRL[,c(1:6)]
head(daacsAnxietyM)
fa.parallel(daacsAnxietyM, fm="pa", fa="fa", main="Anxiety Management Subscale", 
            n.iter=1000, SMC=TRUE, show.legend=TRUE)
```

```{r}
daacsMast<-daacsSRL[,c(7:10)]
head(daacsMast)
fa.parallel(daacsMast, fm="pa", fa="fa", 
            main="Mastery Orientation Subscale", 
            n.iter=1000, SMC=TRUE, show.legend=TRUE)
```
```{r}
daacsSE<-daacsSRL[,c(17:20)]
head(daacsSE)
fa.parallel(daacsSE, fm="pa", fa="fa", main="On-line Learning Self-efficacy Subscale", 
            n.iter=1000, SMC=TRUE, show.legend=TRUE)
```

```{r}
daacsGritP<-daacsSRL[,c(48:51)]
head(daacsGritP)
fa.parallel(daacsGritP, fm="pa", fa="fa", main="Grit Persistance Subscale", 
            n.iter=1000, SMC=TRUE, show.legend=TRUE)
```

```{r}
daacsGritCons<-daacsSRL[,c(52:57)]
head(daacsGritCons)
fa.parallel(daacsGritCons, fm="pa", fa="fa", main="Grit Consistancy Subscale", 
            n.iter=1000, SMC=TRUE, show.legend=TRUE)
```
```{r}
daacsMindset<-daacsSRL[,c(11:16)]
head(daacsMindset)
fa.parallel(daacsMindset, fm="pa", fa="fa", main="Mindset Subscale", n.iter=1000, 
            SMC=TRUE, show.legend=TRUE)
```


```{r}
daacsStrategies<-daacsSRL[,c(35:47)]
head(daacsStrategies)
fa.parallel(daacsStrategies, fm="pa", fa="fa", main="Learning Strategies Scale", 
            n.iter=1000, SMC=TRUE, show.legend=TRUE)
```

```{r}
daacsHelpSk<-daacsSRL[,c(35:37)]
head(daacsHelpSk)
fa.parallel(daacsHelpSk, fm="pa", fa="fa", main="Help Seaking Subscale", 
            n.iter=1000, SMC=TRUE, show.legend=TRUE)
```

```{r}
daacsUndrst<-daacsSRL[,c(38:41)]
head(daacsUndrst)
fa.parallel(daacsUndrst, fm="pa", fa="fa", main="Understanding Subscale", 
            n.iter=1000, SMC=TRUE, show.legend=TRUE)
```

```{r}
daacsManEnv<-daacsSRL[,c(42:44)]
head(daacsManEnv)
fa.parallel(daacsManEnv, fm="pa", fa="fa", main="Managing Environment Subscale", 
            n.iter=1000, SMC=TRUE, show.legend=TRUE)
```

```{r}
daacsTimeMan<-daacsSRL[,c(45:47)]
head(daacsTimeMan)
fa.parallel(daacsTimeMan, fm="pa", fa="fa", main="Time Management Subscale", 
            n.iter=1000, SMC=TRUE, show.legend=TRUE)
```


```{r omega}
omega(daacsSRL)
omega(daacsMetacog)
omega(daacsPlan)
omega(daacsEval)
omega(daacsMonit)
omega(daacsMotiv)
omega(daacsAnxietyM)
omega(daacsMindset)
omega(daacsMast)
omega(daacsSE)
omega(daacsGritP)
omega(daacsGritCons)
omega(daacsStrategies)
omega(daacsHelpSk)
omega(daacsManEnv)
omega(daacsUndrst)
omega(daacsTimeMan)
```


```{r alpha95CI}
alpha(daacsAnxietyM,check.keys=TRUE)
alpha(daacsMindset,check.keys=TRUE)
alpha(daacsMast,check.keys=TRUE)
```

omegaSem(daacsMast) does not run: Error in str2lang(x) : <text>:2:0: unexpected end of input
1: ~ 
   ^
```{r omegaSem}
omegaSem(daacsAnxietyM)
omegaSem(daacsMindset)
```
```

Revelle's beta coefficient and other split-half reliability measures could not be calculated for the total SRL assessment and for the Motivation scale.
```{r splithalf}
spMetac <- splitHalf(daacsMetacog,raw=TRUE, brute=TRUE)
spMetac
hist(spMetac$raw,breaks=101, xlab="Split-half reliability",
main="Split half reliabilities of Metacognition Scale")
spPlan <- splitHalf(daacsPlan,raw=TRUE, brute=TRUE)
spPlan
hist(spPlan$raw,breaks=101, xlab="Split-half reliability",
main="Split half reliabilities of Planning Subscale")
spEval <- splitHalf(daacsEval,raw=TRUE, brute=TRUE)
spEval
hist(spEval$raw,breaks=101, xlab="Split-half reliability",
main="Split half reliabilities of Evaluation Subscale")
spMonit <- splitHalf(daacsMonit,raw=TRUE, brute=TRUE)
spMonit
hist(spMonit$raw,breaks=101, xlab="Split-half reliability",
main="Split half reliabilities of Monitoring Subscale")
spAnx <- splitHalf(daacsAnxietyM,raw=TRUE, brute=TRUE)
spAnx
hist(spAnx$raw,breaks=101, xlab="Split-half reliability",
main="Split half reliabilities of Anxiety Subscale")
spMinds <- splitHalf(daacsMindset,raw=TRUE, brute=TRUE)
spMinds
hist(spMinds$raw,breaks=101, xlab="Split-half reliability",
main="Split half reliabilities of Mindset Subscale")
spMastery <- splitHalf(daacsMast,raw=TRUE, brute=TRUE)
spMastery
hist(spMastery$raw,breaks=101, xlab="Split-half reliability",
main="Split half reliabilities of Mastery Subscale")
spSelfE <- splitHalf(daacsSE,raw=TRUE, brute=TRUE)
spSelfE
hist(spSelfE$raw,breaks=101, xlab="Split-half reliability",
main="Split half reliabilities of Self-Efficacy Subscale")
spGritP <- splitHalf(daacsGritP,raw=TRUE, brute=TRUE)
spGritP
hist(spGritP$raw,breaks=101, xlab="Split-half reliability",
main="Split half reliabilities of Grit Persistency Subscale")
spGritC <- splitHalf(daacsGritCons,raw=TRUE, brute=TRUE)
spGritC
hist(spGritC$raw,breaks=101, xlab="Split-half reliability",
main="Split half reliabilities of Grit Consistency Subscale")
spStrat <- splitHalf(daacsStrategies,raw=TRUE, brute=TRUE)
spStrat
hist(spStrat$raw,breaks=101, xlab="Split-half reliability",
main="Split half reliabilities of Learning Strategies Scale")
spHelpS <- splitHalf(daacsHelpSk,raw=TRUE, brute=TRUE)
spHelpS
hist(spHelpS$raw,breaks=101, xlab="Split-half reliability",
main="Split half reliabilities of Help-Seeking Subscale")
spManEnv <- splitHalf(daacsManEnv,raw=TRUE, brute=TRUE)
spManEnv
hist(spManEnv$raw,breaks=101, xlab="Split-half reliability",
main="Split half reliabilities of Managing Environment Subscale")
spUnderst <- splitHalf(daacsUndrst,raw=TRUE, brute=TRUE)
spUnderst
hist(spUnderst$raw,breaks=101, xlab="Split-half reliability",
main="Split half reliabilities of Metacognition")
spTimeM <- splitHalf(daacsTimeMan,raw=TRUE, brute=TRUE)
spTimeM
hist(spTimeM$raw,breaks=101, xlab="Split-half reliability",
main="Split half reliabilities of Time Management Subscale")
```

