---
title: "DAACS_UA2_UMGC1_Testing for Multivariate Outliers_OR"
author: "Oxana Rosca"
date: "2022-12-16"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(psych)
library(haven)
```

Load the data file
```{r}
global_ua2umgc1 <- readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/global_ua2umgc1.rds")
```

*Verify the File*

Total Number of Participants and Demographics or how many participants and 
variables you have:
```{r}
dim(global_ua2umgc1)
```

Test for duplicate values DAACS_ID
Frequencies: How many of non-duplicated IDs?
```{r}
table(duplicated(global_ua2umgc1$DAACS_ID))
```
Test for empty rows:
```{r}
global_ua2umgc1_Check<-
  global_ua2umgc1[rowSums(is.na(global_ua2umgc1))!=ncol(global_ua2umgc1),]
```
The # of cases in the _check dataframe remains the same; hence, there are no 
empty rows

See the minimum time taken for every assessment IN MINUTES
```{r}
min(global_ua2umgc1$readTime, na.rm = TRUE)
min(global_ua2umgc1$mathTime, na.rm = TRUE)
min(global_ua2umgc1$srlTime, na.rm = TRUE)
min(global_ua2umgc1$writeTime, na.rm = TRUE)
```

Check that only the first attempts are subset:
```{r}
max(global_ua2umgc1$read_attempt, na.rm = TRUE)
max(global_ua2umgc1$math_attempt, na.rm = TRUE)
max(global_ua2umgc1$srl_attempt, na.rm = TRUE)
max(global_ua2umgc1$write_attempt, na.rm = TRUE)
```

*Mahalanobis' distance*

Mahalanobis' distance (mah.distance) is a statistical measure of the extent to which cases 
are multivariate outliers, based on a chi-square distribution, assessed using 
p < .001. The critical chi-square values for 4 degrees of freedom at a critical 
alpha of .001 is 18.47: https://en.wikiversity.org/wiki/Mahalanobis%27_distance.

A maximum mah.distance larger than the critical chi-square value for df = k (the number of 
predictor variables in the model) at a critical alpha value of .001 indicates 
the presence of one or more multivariate outliers.

*Outliers on the Total Scores*

Subset the total scores for four assessments
```{r}
totalScores<-global_ua2umgc1[,c(21,49,236,39)]
```

```{r}
mah.distance<-outlier(totalScores)
outliers_totalScores <- data.frame(totalScores,mah.distance)
pairs.panels(outliers_totalScores,bg=c("grey","blue")[(mah.distance>18.47)+1],
             pch=21,main="Multivariate Outliers for Total Scores")
```
Add the ID variable to the dataset:
```{r}
outliers_totalScores$srlTime <- global_ua2umgc1$srlTime
outliers_totalScores$mathTime <- global_ua2umgc1$mathTime
outliers_totalScores$readTime <- global_ua2umgc1$readTime
outliers_totalScores$writeTime <- global_ua2umgc1$writeTime
outliers_totalScores$DAACS_ID <- global_ua2umgc1$DAACS_ID
```

```{r}
outliers_totalScores <- 
 outliers_totalScores[which(outliers_totalScores$mah.distance>18.47),]
outliers_totalScores
```

*Verify the File*

Duplicate DAACS_IDs
```{r}
table(duplicated(outliers_totalScores$DAACS_ID))
```
Test for empty rows:
```{r}
outliers_totalScores_Check<-
outliers_totalScores[rowSums(is.na(outliers_totalScores))!=ncol(outliers_totalScores),]
```

*Save New File*
```{r}
saveRDS(outliers_totalScores, file = 'MV outliers_totalScores.rds')
write_sav(outliers_totalScores, "MV outliers_totalScores.sav")
write.table(outliers_totalScores, 'MV outliers_totalScores.csv', sep=',')
```

*Outliers on the Math Domains*

Subset the scores for Math Domains
```{r}
df<-global_ua2umgc1[,c(43:49)]
```

```{r}
mah.distance<-outlier(df)
outliers_df <- data.frame(df,mah.distance)
pairs.panels(outliers_df,bg=c("grey","blue")[(mah.distance>24.32)+1],
             gap=0,pch=21,main="Multivariate Outliers for Math Domains")
```
Add the ID variable to the dataset:
```{r}
outliers_df$mathTime <- global_ua2umgc1$mathTime
outliers_df$DAACS_ID <- global_ua2umgc1$DAACS_ID
```

```{r}
outliers_math <- 
 outliers_df[which(outliers_df$mah.distance>26.13),]
outliers_math
```
*Verify the File*
```{r}
table(duplicated(outliers_math$DAACS_ID))
outliers_math_Check<-
outliers_math[rowSums(is.na(outliers_math))!=ncol(outliers_math),]
```

*Save New File*
```{r}
saveRDS(outliers_math, file = 'multivariate outliers_math.rds')
write_sav(outliers_math, "multivariate outliers_math.sav")
write.table(outliers_math, 'multivariate outliers_math.csv', sep=',')
```

*Outliers on Reading Domains*

Subset the scores for Reading Domains
```{r}
df<-global_ua2umgc1[,c(231:236)]
```

```{r}
mah.distance<-outlier(df)
outliers_df <- data.frame(df,mah.distance)
pairs.panels(outliers_df,bg=c("grey","blue")[(mah.distance>22.46)+1],
             gap=0,pch=21,main="Multivariate Outliers on Reading Domains")
```
Add the ID variable to the dataset:
```{r}
outliers_df$readTime <- global_ua2umgc1$readTime
outliers_df$DAACS_ID <- global_ua2umgc1$DAACS_ID
```

```{r}
outliers_read <- 
 outliers_df[which(outliers_df$mah.distance>24.32),]
outliers_read
```
*Verify the File*
```{r}
table(duplicated(outliers_read$DAACS_ID))
outliers_read_Check<-
outliers_read[rowSums(is.na(outliers_read))!=ncol(outliers_read),]
```

*Save New File*
```{r}
saveRDS(outliers_read, file = 'multivariate outliers_read.rds')
write_sav(outliers_read, "multivariate outliers_read.sav")
write.table(outliers_read, 'multivariate outliers_read.csv', sep=',')
```

*Outliers on Writing Criteria*

Subset the scores for Writing Criteria
```{r}
df<-global_ua2umgc1[,c(27:36)]
```

```{r}
mah.distance<-outlier(df)
outliers_df <- data.frame(df,mah.distance)
pairs.panels(outliers_df,bg=c("grey","blue")[(mah.distance>29.59)+1],
             gap=0,pch=21,main="Multivariate Outliers on Writing Criteria")
```
Add the ID variable to the dataset:
```{r}
outliers_df$writeTime <- global_ua2umgc1$writeTime
outliers_df$DAACS_ID <- global_ua2umgc1$DAACS_ID
```

```{r}
outliers_write <- 
 outliers_df[which(outliers_df$mah.distance>24.32),]
outliers_write
```
*Verify the File*
```{r}
table(duplicated(outliers_write$DAACS_ID))
outliers_write_Check<-
outliers_write[rowSums(is.na(outliers_write))!=ncol(outliers_write),]
```
The scales on the graphical outputs of multivariate outliers confirm that there 
are no negative values on the scores, nether values greater than the maximum 
values on the score ranges. There are no weird subjects or data entry errors.

*Save New File*
```{r}
saveRDS(outliers_write, file = 'multivariate outliers_write.rds')
write_sav(outliers_write, "multivariate outliers_write.sav")
write.table(outliers_write, 'multivariate outliers_write.csv', sep=',')
```