---
title: "DAACS_math_Multiple-Attempt-Takers_UA2 and UMGC1_T-test_Sep16_2022_OR"
author: "Oxana Rosca"
date: "2022-14-11"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(haven)
library(dplyr)
library(tidyverse)
library(ggpubr)
library(rstatix)
library(pwr)
```

*Results of the paired t-test*
SRL Total Score result: there is statistically significant difference between 
the first and the second attempts.The second attempt's score is on average 0.124 
point higher than the score for the first attempt. 
The effect size for the paired t-test is Cohen’s d = -0.3652094 (medium)
There is no difference between the total scores from the first and the second 
attempts on math, reading, and writing assessments. That suggests the test-
retest reliability of our assessments, but the power test shows that sample 
sizes are too small to claim the validity evidence. The 16-student sample on 
writing assessment is sufficient to find a large effect size of d>=0.9; the 
30-student sample on math assessment is sufficient to find a large effect size 
of d>=0.6; and the 55-student sample on reading assessment is sufficient to find 
a medium effect size of d>=0.4. None of three samples is to find a medium effect 
size of d=0.3 or smaller.

Load the files with results for all attempts (the daacs.rds contains only the 
results for the first attempts)
*UMGC1*
```{r}
load("data_export/DAACS-Results-umgc_2022-09-16.rda")
#Subset the 1st attempts
daacsumgc1<-daacs[,c(1:21,25:32,36:42,46,48:57,60)]
#To subset the 2nd, 3rd, and 4th attempts later:
math.results.umgc1<-math.results[,-c(10,11)]
read.results.umgc1<-read.results[,-c(9,10)]
srl.results.umgc1<-srl.results[,-c(22,23)]
write.results.umgc1<-write.results[,-c(3,14,15)]
```

calculate the time variables in minutes
```{r}
daacsumgc1$srlTime1<-(daacs$srlCompletionDate-daacs$srlStartDate)/60
daacsumgc1$mathTime1<-(daacs$mathCompletionDate-daacs$mathStartDate)/60
daacsumgc1$readTime1<-(daacs$readCompletionDate-daacs$readStartDate)/60
daacsumgc1$writeTime1<-(daacs$writeCompletionDate-daacs$writeStartDate)/60
srl.results.umgc1$srlTime2<-
              (srl.results$srlCompletionDate-srl.results$srlStartDate)/60
math.results.umgc1$mathTime2<-
          (math.results$mathCompletionDate-math.results$mathStartDate)/60
read.results.umgc1$readTime2<-
          (read.results$readCompletionDate-read.results$readStartDate)/60
write.results.umgc1$writeTime2<-
      (write.results$writeCompletionDate-write.results$writeStartDate)/60
```

To remove the non-numeric substring "sec" from the values of srlTime
```{r}
#for the 1st attempts
time_var_temp <- 
lapply(daacsumgc1[49],function(x)as.numeric(sub("\\s+\\D+$","",x)))
time_var_temp<-as.data.frame(time_var_temp)
daacsumgc1$srlTime1<-time_var_temp$srlTime1
#for the 2nd, 3rd, and 4th attempts
time_var_temp <- 
lapply(srl.results.umgc1[22],function(x)as.numeric(sub("\\s+\\D+$","",x)))
time_var_temp<-as.data.frame(time_var_temp)
srl.results.umgc1$srlTime2<-time_var_temp$srlTime2
```
To remove the non-numeric substring "sec" from the values of mathTime
```{r}
#for the 1st attempts
time_var_temp <- 
lapply(daacsumgc1[50],function(x)as.numeric(sub("\\s+\\D+$","",x)))
time_var_temp<-as.data.frame(time_var_temp)
daacsumgc1$mathTime1<-time_var_temp$mathTime1
#for the 2nd, 3rd, and 4th attempts
time_var_temp <- 
lapply(math.results.umgc1[10],function(x)as.numeric(sub("\\s+\\D+$","",x)))
time_var_temp<-as.data.frame(time_var_temp)
math.results.umgc1$mathTime2<-time_var_temp$mathTime2
```
To remove the non-numeric substring "sec" from the values of readTime
```{r}
#for the 1st attempts
time_var_temp <- 
lapply(daacsumgc1[51],function(x)as.numeric(sub("\\s+\\D+$","",x)))
time_var_temp<-as.data.frame(time_var_temp)
daacsumgc1$readTime1<-time_var_temp$readTime1
#for the 2nd, 3rd, and 4th attempts
time_var_temp <- 
lapply(read.results.umgc1[9],function(x)as.numeric(sub("\\s+\\D+$","",x)))
time_var_temp<-as.data.frame(time_var_temp)
read.results.umgc1$readTime2<-time_var_temp$readTime2
```
To remove the non-numeric substring "sec" from the values of writeTime 
```{r}
#for the 1st attempts
time_var_temp <- 
lapply(daacsumgc1[52],function(x)as.numeric(sub("\\s+\\D+$","",x)))
time_var_temp<-as.data.frame(time_var_temp)
daacsumgc1$writeTime1<-time_var_temp$writeTime1
#for the 2nd, 3rd, and 4th attempts
time_var_temp <- 
lapply(write.results.umgc1[14],function(x)as.numeric(sub("\\s+\\D+$","",x)))
time_var_temp<-as.data.frame(time_var_temp)
write.results.umgc1$writeTime2<-time_var_temp$writeTime2
```

*UA2*
```{r}
load("data_export/DAACS-Results-albany_2022-09-16.rda")
#Subset the 1st attempts
daacsua2<-daacs[,c(1:21,25:32,36:42,46,48:57,60)]
#To subset the 2nd, 3rd, and 4th attempts later:
math.results.ua2<-math.results[,-c(10,11)]
read.results.ua2<-read.results[,-c(9,10)]
srl.results.ua2<-srl.results[,-c(22,23)]
write.results.ua2<-write.results[,-c(3,14,15)]
```

calculate the time variables in minutes
```{r}
daacsua2$srlTime1<-(daacs$srlCompletionDate-daacs$srlStartDate)
daacsua2$mathTime1<-(daacs$mathCompletionDate-daacs$mathStartDate)
daacsua2$readTime1<-(daacs$readCompletionDate-daacs$readStartDate)/60
daacsua2$writeTime1<-(daacs$writeCompletionDate-daacs$writeStartDate)
srl.results.ua2$srlTime2<-
              (srl.results$srlCompletionDate-srl.results$srlStartDate)
math.results.ua2$mathTime2<-
          (math.results$mathCompletionDate-math.results$mathStartDate)
read.results.ua2$readTime2<-
          (read.results$readCompletionDate-read.results$readStartDate)/60
write.results.ua2$writeTime2<-
      (write.results$writeCompletionDate-write.results$writeStartDate)/60
```

To remove the non-numeric substring "sec" from the values of srlTime
```{r}
#for the 1st attempts
time_var_temp <- 
lapply(daacsua2[49],function(x)as.numeric(sub("\\s+\\D+$","",x)))
time_var_temp<-as.data.frame(time_var_temp)
daacsua2$srlTime1<-time_var_temp$srlTime1
#for the 2nd, 3rd, and 4th attempts
time_var_temp <- 
lapply(srl.results.ua2[22],function(x)as.numeric(sub("\\s+\\D+$","",x)))
time_var_temp<-as.data.frame(time_var_temp)
srl.results.ua2$srlTime2<-time_var_temp$srlTime2
```
To remove the non-numeric substring "sec" from the values of mathTime
```{r}
#for the 1st attempts
time_var_temp <- 
lapply(daacsua2[50],function(x)as.numeric(sub("\\s+\\D+$","",x)))
time_var_temp<-as.data.frame(time_var_temp)
daacsua2$mathTime1<-time_var_temp$mathTime1
#for the 2nd, 3rd, and 4th attempts
time_var_temp <- 
lapply(math.results.ua2[10],function(x)as.numeric(sub("\\s+\\D+$","",x)))
time_var_temp<-as.data.frame(time_var_temp)
math.results.ua2$mathTime2<-time_var_temp$mathTime2
```
To remove the non-numeric substring "sec" from the values of readTime
```{r}
#for the 1st attempts
time_var_temp <- 
lapply(daacsua2[51],function(x)as.numeric(sub("\\s+\\D+$","",x)))
time_var_temp<-as.data.frame(time_var_temp)
daacsua2$readTime1<-time_var_temp$readTime1
#for the 2nd, 3rd, and 4th attempts
time_var_temp <- 
lapply(read.results.ua2[9],function(x)as.numeric(sub("\\s+\\D+$","",x)))
time_var_temp<-as.data.frame(time_var_temp)
read.results.ua2$readTime2<-time_var_temp$readTime2
```
To remove the non-numeric substring "sec" from the values of writeTime 
```{r}
#for the 1st attempts
time_var_temp <- 
lapply(daacsua2[52],function(x)as.numeric(sub("\\s+\\D+$","",x)))
time_var_temp<-as.data.frame(time_var_temp)
daacsua2$writeTime1<-time_var_temp$writeTime1
#for the 2nd, 3rd, and 4th attempts
time_var_temp <- 
lapply(write.results.ua2[14],function(x)as.numeric(sub("\\s+\\D+$","",x)))
time_var_temp<-as.data.frame(time_var_temp)
write.results.ua2$writeTime2<-time_var_temp$writeTime2
```

*Adjusting UA2's IDs*
To distinguish the DAACS_IDs of different colleges, always add 10,000 to UA2 
DAACS_IDs:
```{r}
daacsua2$DAACS_ID<-daacsua2$DAACS_ID+10000
math.results.ua2$DAACS_ID<-math.results.ua2$DAACS_ID+10000
read.results.ua2$DAACS_ID<-read.results.ua2$DAACS_ID+10000
srl.results.ua2$DAACS_ID<-srl.results.ua2$DAACS_ID+10000
write.results.ua2$DAACS_ID<-write.results.ua2$DAACS_ID+10000
```

*Duplicates*
Test for duplicate values
Frequencies: How many of non-duplicated IDs?
```{r}
table(duplicated(daacsua2$DAACS_ID))
```

```{r}
table(duplicated(daacsumgc1$DAACS_ID))
```
*Merge*
Combine the data from two colleges on the first attempts 
```{r}
daacsua2umgc1<-rbind(daacsua2,daacsumgc1)
```

*Attempts*
How many of each number of UA2 math attempts?
```{r}
table(math.results.ua2$attempt,useNA = 'ifany') %>% print() %>% prop.table()*100
```
How many of each number of UMGC1 math attempts?
```{r}
table(math.results.umgc1$attempt,useNA ='ifany')%>%print() %>% prop.table()* 100
```

How many of each number of UA2 reading attempts?
```{r}
table(read.results.ua2$attempt,useNA ='ifany') %>% print() %>% prop.table()* 100
```
How many of each number of UMGC1 reading attempts?

```{r}
table(read.results.umgc1$attempt,useNA='ifany')%>% print() %>% prop.table()* 100
```

How many of each number of UA2 writing attempts?
```{r}
table(write.results.ua2$attempt,useNA='ifany') %>% print() %>% prop.table()* 100
```
How many of each number of UMGC1 writing attempts?
```{r}
table(write.results.umgc1$attempt,useNA='ifany')%>%print() %>% prop.table()* 100
```

How many of each number of UA2 SRL attempts?
```{r}
table(srl.results.ua2$attempt,useNA='ifany') %>% print() %>% prop.table()* 100
```
How many of each number of UMGC1 SRL attempts?
```{r}
table(srl.results.umgc1$attempt,useNA='ifany')%>%print() %>% prop.table()* 100
```

*Subsetting the 2nd, 3rd, and 4th attempts* 
```{r}
math.results.ua2MultAttWide <- math.results.ua2 [math.results.ua2$attempt == "2",]
math.results.umgc1MultAttWide<-math.results.umgc1[math.results.umgc1$attempt =="2",]
read.results.ua2MultAttWide <- read.results.ua2 %>% filter(attempt != 1)
read.results.umgc1MultAttWide <- read.results.umgc1 %>% filter(attempt != 1)
write.results.ua2MultAttWide <- write.results.ua2 %>% filter(attempt != 1)
write.results.umgc1MultAttWide <- write.results.umgc1 %>% filter(attempt != 1)
srl.results.ua2MultAttWide <- srl.results.ua2 %>% filter(attempt != 1)
srl.results.umgc1MultAttWide <- srl.results.umgc1 %>% filter(attempt != 1)
```

merge the data from two colleges
```{r}
math.results.ua2umgc1MultAttWide<-
  rbind(math.results.ua2MultAttWide,math.results.umgc1MultAttWide)
read.results.ua2umgc1MultAttWide<-
  rbind(read.results.ua2MultAttWide,read.results.umgc1MultAttWide)
write.results.ua2umgc1MultAttWide <- 
  rbind(write.results.ua2MultAttWide,write.results.umgc1MultAttWide)
srl.results.ua2umgc1MultAttWide <-
  rbind(srl.results.ua2MultAttWide,srl.results.umgc1MultAttWide)
```

merge the all attempts of the students who took more than one attempt
```{r}
math.ua2umgc1MultAttWide<-merge(daacsua2umgc1[,c(1,22:29,50)],
              math.results.ua2umgc1MultAttWide,by='DAACS_ID',all.y=TRUE)
read.ua2umgc1MultAttWide<-merge(daacsua2umgc1[,c(1,30:36,51)],
              read.results.ua2umgc1MultAttWide,by='DAACS_ID',all.y=TRUE)
srl.ua2umgc1MultAttWide<-merge(daacsua2umgc1[,c(1:21,49)],
              srl.results.ua2umgc1MultAttWide,by='DAACS_ID',all.y=TRUE)
write.ua2umgc1MultAttWide<-merge(daacsua2umgc1[,c(1,37:48,52)],
            write.results.ua2umgc1MultAttWide,by='DAACS_ID',all.y=TRUE)
```

*Rename*
rename the variables
```{r}
colnames(read.ua2umgc1MultAttWide) <- c("DAACS_ID","attempt.1",
         "structure.1","inference.1","language.1","purpose.1","ideas.1",
         "readTotal.1","readTime.1","attempt.2","structure.2","inference.2",
         "language.2","purpose.2","ideas.2","readTotal.2","readTime.2")
colnames(math.ua2umgc1MultAttWide) <- c("DAACS_ID","attempt.1",
        "word_problems.1" ,"lines_and_functions.1","variables_and_equations.1",
        "number_and_calculation.1","statistics.1","geometry.1","mathTotal.1",
        "mathTime.1","attempt.2","word_problems.2" ,"lines_and_functions.2",
        "variables_and_equations.2","number_and_calculation.2","statistics.2",
        "geometry.2","mathTotal.2","mathTime.2")
colnames(write.ua2umgc1MultAttWide) <- c("DAACS_ID","attempt.1","summary.1",
          "suggestions.1","structure.1","transitions.1","ideas.1","cohesion.1",
          "correct.1","complexity.1","usage.1","punctuation.1","writeTotal.1",
          "writeTime.1","attempt.2","summary.2","suggestions.2","structure.2",
          "transitions.2","ideas.2","cohesion.2","correct.2","complexity.2",
          "usage.2","punctuation.2","writeTotal.2","writeTime.2")
colnames(srl.ua2umgc1MultAttWide) <- c("DAACS_ID","attempt.1","strategies.1",
        "motivation.1","metacognition.1","selfefficacy.1","managing_time.1",
        "help_seeking.1","managing_environment.1","understanding.1","anxiety.1",
        "mastery_orientation.1","mindset.1","evaluation.1","monitoring.1",
        "planning.1","self_efficacy_for_mathematics2.1",
        "selfefficacy_for_online_learning.1","selfefficacy_for_reading.1",
        "selfefficacy_for_writing.1","srlTotal.1",
        "srlTime.1","attempt.2","strategies.2","motivation.2","metacognition.2",
        "selfefficacy.2","managing_time.2","help_seeking.2",
        "managing_environment.2","understanding.2","anxiety.2",
        "mastery_orientation.2","mindset.2","evaluation.2","monitoring.2",
        "planning.2","self_efficacy_for_mathematics.2",
        "selfefficacy_for_online_learning.2","selfefficacy_for_reading.2",
        "selfefficacy_for_writing.2","srlTotal.2","srlTime.2")                                          
```

*Saving New Datasets*
```{r}
# saveRDS(math.ua2umgc1MultAttWide, file = 'math.ua2umgc1MultAttWide.rds')
# write_sav(math.ua2umgc1MultAttWide, "math.ua2umgc1MultAttWide.sav")
# write.table(math.ua2umgc1MultAttWide,'math.ua2umgc1MultAttWide.csv',sep=',')
# saveRDS(read.ua2umgc1MultAttWide, file = 'read.ua2umgc1MultAttWide.rds')
# write_sav(read.ua2umgc1MultAttWide, "read.ua2umgc1MultAttWide.sav")
# write.table(read.ua2umgc1MultAttWide,'read.ua2umgc1MultAttWide.csv',sep=',')
# saveRDS(srl.ua2umgc1MultAttWide, file = 'srl.ua2umgc1MultAttWide.rds')
# write_sav(srl.ua2umgc1MultAttWide, "srl.ua2umgc1MultAttWide.sav")
# write.table(srl.ua2umgc1MultAttWide,'srl.ua2umgc1MultAttWide.csv',sep=',')
# saveRDS(write.ua2umgc1MultAttWide, file = 'write.ua2umgc1MultAttWide.rds')
# write_sav(write.ua2umgc1MultAttWide, "write.ua2umgc1MultAttWide.sav")
# write.table(write.ua2umgc1MultAttWide,'write.ua2umgc1MultAttWide.csv',sep=',')
```

*Transform*
Transform the data from wide into long datasets with the 1st and 2nd attempts.

Remove the 3rd and 4th attempts.
```{r}
read.ua2umgc1.2attWide<- 
  read.ua2umgc1MultAttWide[read.ua2umgc1MultAttWide$attempt.2== 2,]
math.ua2umgc1.2attWide<- 
  math.ua2umgc1MultAttWide[math.ua2umgc1MultAttWide$attempt.2== 2,]
srl.ua2umgc1.2attWide<- 
  srl.ua2umgc1MultAttWide[srl.ua2umgc1MultAttWide$attempt.2== 2,]
write.ua2umgc1.2attWide<- 
  write.ua2umgc1MultAttWide[write.ua2umgc1MultAttWide$attempt.2== 2,]
```

split each file into two files: one file per attempt. Then combine those two 
files again into a long dataset.
```{r}
#Reading
read.ua2umgc1.1stAtt<-read.ua2umgc1.2attWide[,c(1:9)]
read.ua2umgc1.2ndAtt<-read.ua2umgc1.2attWide[,c(1,10:17)]
colnames(read.ua2umgc1.1stAtt)<-c("DAACS_ID","attempt","structure","inference",
                        "language","purpose","ideas","readTotal","readTime")
colnames(read.ua2umgc1.2ndAtt)<-c("DAACS_ID","attempt","structure","inference",
                        "language","purpose","ideas","readTotal","readTime")
read.ua2umgc1.2attLong<-rbind(read.ua2umgc1.1stAtt,read.ua2umgc1.2ndAtt)
#Writing
write.ua2umgc1.1stAtt<-write.ua2umgc1.2attWide[,c(1:14)]
write.ua2umgc1.2ndAtt<-write.ua2umgc1.2attWide[,c(1,15:27)]
colnames(write.ua2umgc1.1stAtt)<-c("DAACS_ID","attempt","summary","suggestions",
            "structure","transitions","ideas","cohesion","correct","complexity",
            "usage","punctuation","writeTotal","writeTime")
colnames(write.ua2umgc1.2ndAtt)<-c("DAACS_ID","attempt","summary","suggestions",
            "structure","transitions","ideas","cohesion","correct","complexity",
            "usage","punctuation","writeTotal","writeTime")
write.ua2umgc1.2attLong<-rbind(write.ua2umgc1.1stAtt,write.ua2umgc1.2ndAtt)
#Math
math.ua2umgc1.1stAtt<-math.ua2umgc1.2attWide[,c(1:10)]
math.ua2umgc1.2ndAtt<-math.ua2umgc1.2attWide[,c(1,11:19)]
colnames(math.ua2umgc1.1stAtt)<-c("DAACS_ID","attempt","word_problems",
      "lines_and_functions","variables_and_equations","number_and_calculation",
      "statistics","geometry","mathTotal","mathTime")
colnames(math.ua2umgc1.2ndAtt)<-c("DAACS_ID","attempt","word_problems",
      "lines_and_functions","variables_and_equations","number_and_calculation",
      "statistics","geometry","mathTotal","mathTime")
math.ua2umgc1.2attLong<-rbind(math.ua2umgc1.1stAtt,math.ua2umgc1.2ndAtt)
#SRL
srl.ua2umgc1.1stAtt<-srl.ua2umgc1.2attWide[,c(1:22)]
srl.ua2umgc1.2ndAtt<-srl.ua2umgc1.2attWide[,c(1,23:43)]
colnames(srl.ua2umgc1.1stAtt)<-c("DAACS_ID","attempt","strategies",
    "motivation","metacognition","selfefficacy","managing_time","help_seeking",
    "managing_environment","understanding","anxiety","mastery_orientation",
    "mindset","evaluation","monitoring","planning",
    "self_efficacy_for_mathematics","selfefficacy_for_online_learning",
    "selfefficacy_for_reading","selfefficacy_for_writing","srlTotal","srlTime")
colnames(srl.ua2umgc1.2ndAtt)<-c("DAACS_ID","attempt","strategies",
    "motivation","metacognition","selfefficacy","managing_time","help_seeking",
    "managing_environment","understanding","anxiety","mastery_orientation",
    "mindset","evaluation","monitoring","planning",
    "self_efficacy_for_mathematics","selfefficacy_for_online_learning",
    "selfefficacy_for_reading","selfefficacy_for_writing","srlTotal","srlTime")
srl.ua2umgc1.2attLong<-rbind(srl.ua2umgc1.1stAtt,srl.ua2umgc1.2ndAtt)
```

*Research Question*
Is there difference between the first and the second attempts' scores?

*Group Mean and SD*
summary statistics by groups

Reading
```{r}
read.ua2umgc1.2attLong %>%
  group_by(attempt) %>%
  get_summary_stats(c(2:8), type = "mean_sd")
```

Writing
```{r}
write.ua2umgc1.2attLong %>%
  group_by(attempt) %>%
  get_summary_stats(c(2:13), type = "mean_sd")
```
Math
```{r}
math.ua2umgc1.2attLong %>%
  group_by(attempt) %>%
  get_summary_stats(c(2:9), type = "mean_sd")
```

SRL
```{r}
srl.ua2umgc1.2attLong %>%
  group_by(attempt) %>%
  get_summary_stats(c(2:21), type = "mean_sd")
```

*Paired T-test*
Reading Total Score result (N=49): there is no difference between the first and the 
second attempts.
```{r}
readTtest <- t.test(readTotal ~ attempt,data = read.ua2umgc1.2attLong,paired = TRUE)
readTtest
```
Math Total Score result (N=30): there is no difference between the first and the 
second attempts.
```{r}
mathTtest <- t.test(mathTotal ~ attempt,data = math.ua2umgc1.2attLong,paired = TRUE)
mathTtest
```
Writing Total Score result (N=15): there is no difference between the first and the 
second attempts.
```{r}
writeTtest <- t.test(writeTotal ~ attempt,data = write.ua2umgc1.2attLong,paired = TRUE)
writeTtest
```
SRL Total Score result (N=92): there is statistically significant difference between 
the first and the second attempts.The second attempt's score is on average 0.124 
point higher than the score for the first attempt. 
```{r}
srlTtest <- t.test(srlTotal ~ attempt,data = srl.ua2umgc1.2attLong,paired = TRUE)
srlTtest
```
Another way to run a t-test

```{r}
srlT.test <- srl.ua2umgc1.2attLong %>% 
  t_test(srlTotal ~ attempt,paired = TRUE) %>%
  add_significance()
srlT.test
```

*Effect Size*

The effect size (Cohen’s d) for a paired-samples t-test can be calculated by 
dividing the mean difference by the standard deviation of the difference.
```{r}
srl.ua2umgc1.2attLong %>% cohens_d(srlTotal ~ attempt, paired = TRUE)
```

*Visualize the Results*

Two ways to build a boxplot:
1.
```{r}
bxp1 <- ggpaired(srl.ua2umgc1.2attLong, x = "attempt", y = "srlTotal", 
         order = c("1", "2"),
         ylab = "srlTotal", xlab = "Attempt #")
bxp1
```

```{r}
srlT.test <- srlT.test %>% add_xy_position(x = "attempt")
bxp1 + 
  stat_pvalue_manual(srlT.test, tip.length = 0) +
  labs(subtitle = get_test_label(srlT.test, detailed= TRUE))
```

2.
```{r}
bxp2 <- ggboxplot(
  srl.ua2umgc1.2attLong, x = "attempt", y = "srlTotal", 
  ylab = "srlTotal", xlab = "Attempt #", add = "jitter"
  )
bxp2
```

```{r}
srlT.test <- srlT.test %>% add_xy_position(x = "attempt")
bxp2 + 
  stat_pvalue_manual(srlT.test, tip.length = 0) +
  labs(subtitle = get_test_label(srlT.test, detailed = TRUE))
```

Can we interpret the results of insignificant results of the t-tests on math, 
reading, and writing assessment as an evidence of a test-retest validity?
It depends on whether the small samples are sufficient or have enough 
statistical power.

*Power Test*
The desired power level is typically 0.8

The 16-student sample on writing assessment is sufficient to find a large effect 
size of d>=0.9, but is too small to find a medium effect size of d=0.3.
```{r}
pwr.t.test(n=16,d=0.9,sig.level=0.05,type="paired",alternative="two.sided")
```
```{r}
pwr.t.test(n=16,d=0.3,sig.level=0.05,type="paired",alternative="two.sided")
```
The 30-student sample on math assessment is sufficient to find a large effect 
size of d>=0.6, but is too small to find a medium effect size of d=0.3.
```{r}
pwr.t.test(n=30,d=0.6,sig.level=0.05,type="paired",alternative="two.sided")
```
```{r}
pwr.t.test(n=30,d=0.3,sig.level=0.05,type="paired",alternative="two.sided")
```
The 55-student sample on reading assessment is sufficient to find a medium 
effect size of d>=0.4, but is too small to find a medium effect size of d=0.3.
```{r}
pwr.t.test(n=55,d=0.4,sig.level=0.05,type="paired",alternative="two.sided")
```

```{r}
pwr.t.test(n=55,d=0.3,sig.level=0.05,type="paired",alternative="two.sided")
```
The 95-student sample on srl assessment is sufficient to find a medium effect 
size of d>=0.3, but is too small to find a small effect size of d=0.2.
```{r}
pwr.t.test(n=95,d=0.3,sig.level=0.05,type="paired",alternative="two.sided")
```

```{r}
pwr.t.test(n=95,d=0.2,sig.level=0.05,type="paired",alternative="two.sided")
```