---
title: "DAACS_read_DataOrganizing_UMGC1_Sep16_2022_OR"
author: "Oxana Rosca"
date: "2022-10-09"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(psych)
library(ggplot2)
library(maditr)
library(stringr)
library(haven)
```

If needed:
setwd("D:OneDrive - University at Albany - SUNY/WorkDirectory")

Load data files
```{r}
load("data_export/DAACS-Results-umgc_2022-09-16.rda")
```

Use str_replace() method from stringr package to replace part of a column string 
with another string in R DataFrame.
```{r}
read.items$qid <- str_replace(read.items$qid,"Q", "rQ")
```

*Duplicates*
Test for duplicate values in read.items.response
Frequencies: How many of non-duplicated IDs?
```{r}
table(duplicated(daacs$DAACS_ID))
```

```{r}
table(duplicated(read.items$DAACS_ID))
```
read.items is a long dataset with many rows per a test-taker

*Attempts*
How many of each number of attempts?
```{r}
table(read.items$attempt, useNA = 'ifany') %>% print() %>% prop.table()* 100
```
Select the first attempts only
```{r}
read.items <- read.items [read.items$attempt == "1",]
```

*Restructure*
re-structure =long dataset from wide dataset
```{r}
umgc1ReadDaacs <- dcast(read.items,DAACS_ID ~ qid,value.var = 'score')
```

*Merge*
Using all.y = TRUE so that we use only students provided from 
umgc1. These are all newly enrolled students' data on Sep 16th, 2022 (Removing 
all students that did not take read assessment)
```{r}
umgc1ReadDaacs <- merge(daacs,umgc1ReadDaacs,by = 'DAACS_ID', all.y = TRUE)
```

*Test Time*
Calculate test time in minutes per student:
```{r}
umgc1ReadDaacs$readTime= (umgc1ReadDaacs$readCompletionDate - 
                            umgc1ReadDaacs$readStartDate)/60
```

To remove the non-numeric substring "sec" from the values of readTime
```{r}
time_var_temp <- 
lapply(umgc1ReadDaacs[242],function(x)as.numeric(sub("\\s+\\D+$","",x)))
time_var_temp<-as.data.frame(time_var_temp)
View(time_var_temp)
umgc1ReadDaacs$readTime<-time_var_temp$readTime
View(umgc1ReadDaacs)
```

see the minimum value IN MINUTES

```{r}
min(umgc1ReadDaacs$readTime)
```

What is the shortest time IN MINUTES for a student to get a perfect score
```{r}
min(umgc1ReadDaacs[umgc1ReadDaacs$readTotal == 1.0,]$readTime)
```
What is the shortest time IN MINUTES for a student to get at least 70%
```{r}
min(umgc1ReadDaacs[umgc1ReadDaacs$readTotal >= .7,]$readTime)
```
How many students took less than 3.5 minutes?
```{r}
nrow(umgc1ReadDaacs[umgc1ReadDaacs$readTime <= 3.5,])
```
To create a separate dataset of speedy students,
1)Create a vector of the row numbers of the speedy students:
```{r}
speedy<-which (umgc1ReadDaacs$readTime <= 3.5)
```

2)subset the rows of the speedy students as a dataframe:
```{r}
umgc1ReadSpeedy<-umgc1ReadDaacs[speedy, ]
umgc1ReadSpeedy[,c(1,42,242)]
```

```{r}
umgc1ReadSpeedy$DAACS_ID
```

11 speedy students with DAACS_ID 34, 174, 204, 396  428, 522, 745, 807,  984, 
1011, and 1032 took less than 3.5 minutes for the reading assessment and less 
than 3 minutes for the math assessment.
11 speedy students with DAACS_ID 48,  194, 326,  505,  599,  614,  657,  804,  
986, 1022, and 1057 took less than 3 minutes for the math assessment.

Remove 22 speedy students (who completed the assesments in 3.5 minutes or less)
```{r}
umgc1ReadDaacs <- umgc1ReadDaacs[umgc1ReadDaacs$readTime > 3.5,]
```


*Total Score*
Histogram of the reading scores in points
```{r}
ggplot(umgc1ReadDaacs, aes(x = readTotal)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('Read Total') +   
                    ylab('Number of Students')
```
Cut the variable of scores into three categories of dots
```{r}
umgc1ReadDaacs$readTotalDots <- cut(umgc1ReadDaacs$readTotal,
                              breaks=c(0, 0.7, 0.9, 1),labels=c('1', '2', '3'))
```

To build a bar-plot of the reading scores in dots

```{r}
table(umgc1ReadDaacs$readTotalDots)
```

```{r}
barplot(table(umgc1ReadDaacs$readTotalDots),
        main="UMGC1 Reading Total Score in Dots",
          xlab="Read Total in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```

To check if there are empty rows:
```{r}
umgc1ReadDaacs_Check<-
  umgc1ReadDaacs[rowSums(is.na(umgc1ReadDaacs))!=ncol(umgc1ReadDaacs),]
```
Comparing the # of cases, there are no empty rows

*Save New File*
Adding a variable of college and saving the new data file:
```{r}
umgc1ReadDaacs$college <- 'UMGC1'
saveRDS(umgc1ReadDaacs, file = 'umgc1ReadDaacs.rds')
write_sav(umgc1ReadDaacs, "umgc1ReadDaacs.sav")
write.table(umgc1ReadDaacs, 'umgc1ReadDaacs.csv', sep=',')
saveRDS(umgc1ReadSpeedy, file = 'umgc1ReadSpeedy.rds')
write_sav(umgc1ReadSpeedy, "umgc1ReadSpeedy.sav")
write.table(umgc1ReadSpeedy, 'umgc1ReadSpeedy.csv', sep=',')
```

*Total Number of Participants and Demographics*
how many paricipants and variables you have 
```{r}
dim(umgc1ReadDaacs)
```