---
title: "DAACS_Writing_DataOrganizing_UA2_Sep16_2022_OR"
author: "Oxana Rosca"
date: "2022-12-02"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


*This script must be run only after* 
*the "DAACS_SRL_DataOrganizing-Descriptives_UA2_Sep 16_2022_OR.r" and*
*before the "DAACS_Combining Colleges into Global and Speedy datasets_OR.r"*

```{r}
library(maditr)
library(ggplot2)
library(haven)
```

#setwd("D:OneDrive - University at Albany - SUNY/WorkDirectory")

Because writing assessment could be taken only after taking the SRL survey, we 
do not need to create a separate dataset for students who took writing 
assessments. We need only to create the variables of total writing score in dots 
and writeTime and add them to the SRL dataset.


Load data files
```{r}
load("data_export/DAACS-Results-albany_2022-09-16.rda")
#load("D:/OneDrive - University at Albany -SUNY/WorkDirectory/data_export/DAACS-Results-albany_2022-09-16.rda")
#load("data_export/ua2SRLDaacs.rds")
#load("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/ua2SRLDaacs.rds")
ua2SRLDaacs <- 
  readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/ua2SRLDaacs.rds")
```


*Duplicates*
Test for duplicate values in write.results
Frequencies: How many of non-duplicated IDs?
```{r}
table(duplicated(write.results$DAACS_ID))
```
There are 4 duplicated DAACS_ID in write.results (they are the second attempts)

*Attempts*
How many of each number of attempts?
```{r}
table(write.results$attempt, useNA = 'ifany') %>% 
  print() %>% prop.table()* 100
```
The ua2SRLDaacs dataset is a subset of all students from daacs.rds who took 
SRL assessment It includes all writing scores from the first attempts of all 
students who took writing assessment. 

*Test Time*
Calculate test time in minutes per student:
```{r}
ua2SRLDaacs$writeTime= (ua2SRLDaacs$writeCompletionDate - 
                            ua2SRLDaacs$writeStartDate)
```

To remove the non-numeric substring "min" from the values of writeTime 
```{r}
time_var_temp <- 
lapply(ua2SRLDaacs[83],function(x)as.numeric(sub("\\s+\\D+$","",x)))
time_var_temp<-as.data.frame(time_var_temp)
View(time_var_temp)
ua2SRLDaacs$writeTime<-time_var_temp$writeTime
View(ua2SRLDaacs)
```

see the minimum value IN MINUTES
```{r}
min(ua2SRLDaacs$writeTime, na.rm = TRUE)
```
*Total Score*
Histogram of the writing total scores
```{r}
library(ggplot2)
ggplot(ua2SRLDaacs, aes(x = writeTotal)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('Write Total') +   
                    ylab('Number of Students')
```
Cut the variable of scores into three categories of dots
```{r}
ua2SRLDaacs$writeTotalDots <- cut(ua2SRLDaacs$writeTotal,
                            breaks=c(0, 0.33, 0.66, 1),labels=c('1', '2', '3'))
```

To build a bar-plot of the reading scores in dots

```{r}
table(ua2SRLDaacs$writeTotalDots)
```

```{r}
barplot(table(ua2SRLDaacs$writeTotalDots),
        main="ua2 Write Total Score in Dots",
        xlab="Write Total in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```

To check if there are empty rows:
```{r}
ua2SRLDaacs_Check<-
  ua2SRLDaacs[rowSums(is.na(ua2SRLDaacs))!=ncol(ua2SRLDaacs),]
```
Comparing the # of cases, there are no empty rows

*Save New File*

```{r}
saveRDS(ua2SRLDaacs, file = 'ua2SRLDaacs.rds')
write_sav(ua2SRLDaacs, "ua2SRLDaacs.sav")#library(haven)
write.table(ua2SRLDaacs, 'ua2SRLDaacs.csv', sep=',')
```