---
title: "DAACS_UA2_UMGC1_SRL Assessment_Parallel Analysis, EFA, and CFA"
author: "Oxana Rosca"
date: "2023-01-31"
output:
  pdf_document: default
  html_document: default
  word_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Assessment of factor structure
Furr (2014):
A scale's dimensionality, or factor structure, refers to the number 
and nature of the variables reflected in its items. 
a) Dimensionality should be evaluated and considered in scale construction, use, 
and evaluation
b) Coefficient alpha is not an index of unidimensionality, the “eigenvalue 
greater than one” rule should be avoided, and oblique rotations are preferable 
to orthogonal rotations.
Each dimension should be scored separately, with each requiring psychometric 
evaluation. That is, each score obtained from a scale should reflect a single 
coherent psychological variable. If a score reflects a blend of non-correlated 
dimensions, then its psychological meaning is highly ambiguous. Thus, a 
unidimensional scale produces a single score representing the lone dimension 
reflected in its items.
If dimensions are correlated robustly (reflecting some shared deeper 
psychological variable), then scores from those dimensions might be combined to 
form a score reflecting their shared psychological variable.

## The SRL assessment consists of 4 scales and 14 subscales.

## Results
The results of parallel analyses of SRL Assessment with the scores of four 
scales (motivation, metacognition, learning strategies, and self-efficacy) as 
indicators suggest 2 factors in the SRL assessment. However, the theoretical 
model assumes a 4-factor structure. 
A probable next step: a second-order CFA to test two second-order factors.


Parallel Analyses of SRL Assessment with 14 subscales' scores as indicators 
(Planning, Monitoring, Evaluating, Mastery, Mindset, Anxiety, Environment, 
The subscales of Planning, Monitoring, Evaluating, Mastery, Mindset, Anxiety, 
Environment, Time, Understanding, Help-seeking, Self-Efficacy for Math, 
Self-Efficacy for Reading, Self-Efficacy for Writing, and Self-Efficacy for 
Online Learning) suggests a four-factor structure of the SRL Assessment, which 
corresponds to the theoretical model. 

Exploratory Factor Analyses (EFA) of SRL Assessment (14 subscales):The 1-, 2-, 
3-, and 9-factor models have a poor fit to the data; The 4-, 5-, 6-, 7-, and 
8-factor models have a good fit to the data. The 4-factor model presents the 
closest  factor structure to the theoretical model. 
The scores of monitoring, evaluation, and planning always load on the same 
factor in 4- and 5-factor EFAs, just as the theoretical model states (the 
metacognition factor).

Three self-efficacy scores of reading, writing, and online learning also always 
load on a single factor, in accordance with the theoretical model (the self-
efficasy factor).

However, the srl_self_efficacy_for_mathematics2 never loads on the the same 
factor with other three indicators of the self-efficacy. 
The construct of motivation is the least present in all EFAs; 
The indicator of srl_mindset tends to lack loading on any factor.

The 4-factor CFA model has a poor fit. The modification indices of the 4-factor 
CFA1 suggested assigning  anxiety to the metacognition factor (CFA2).
The modification didn't improve the fit statistics, but the modification 
indecies of the CFA2 suggested  assigning  anxiety to the self-efficacy factor 
(CFA3). That modification improved one (SRMR) of the three fit statistics to an 
acceptable level. 
Other  modification indices suggested correlations between: managing_environment 
and managing_time, anxiety and math self-efficacy, reading self-efficacy and 
writing self-efficacy, and planning and evaluation. None of those modifications 
improved the fit sufficiently.

## The next steps: 
1.Run a bifactor model to test the SRL scale for general factor saturation.
2.Run a second-order CFA including all items of every SRL sub-scale.
3.After clarifying the scale's structure (CFA), examine the reliability and 
validity of each dimension through a series of studies (Furr, 2014).

```{r}
library(psych)
library(psychTools)
library(lavaan)
library(semPlot)
library(dplyr)
```
Test for the unidimensionality and number of factors in your data using parallel
analysis and Exploratory FA
Load the data file
```{r}
global_ua2umgc1 <- 
readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/global_ua2umgc1.rds")
```

## Results
Results: The results of parallel analyses of SRL Assessment with the scores of 
four scales (motivation, metacognition, learning strategies, and self-efficacy) 
as indicators suggest 2 factors in the SRL assessment. However, the theoretical 
model assumes a 4-factor structure.

## Four scales of SRL Assessment
Motivation, metacognition, learning strategies, and self-efficacy scales suggest 
two-factor structure. 

### Parallel Analyses of SRL Assessment with the 4 scales' scores as indicators. 
Motivation, metacognition, learning strategies, and self-efficacy. 

#### Combined Sample (UA2 and UMGC1) Parallel Analysis of SRL Assnt (4 scales)
```{r}
fa.parallel(global_ua2umgc1[,c(3:6)],fa="fa",fm="ml",n.iter=1000,
    main="Parallel Analysis Scree plot for SRL Assnt (4 scales), UA2 and UMGC1")
```

#### UMGC1 Sample Parallel Analysis of SRL Assessment (four scales)
```{r}
fa.parallel(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(3:6)],fm="ml",
          fa="fa",n.iter=1000,
  main="Parallel Analysis Scree plot for SRL Assessment (four scales), UMGC1")
```

#### UA2 Sample Parallel Analysis of SRL Assessment (four scales)
```{r}
fa.parallel(global_ua2umgc1[global_ua2umgc1$college=="UA2",c(3:6)],fa="fa",
                fm="ml",n.iter=1000,
    main="Parallel Analysis Scree plot for SRL Assessment (four scales), UA2")
```

### Exploratory Factor Analyses (EFA) of SRL Assessment (four scales)
Run only 1- and 2-factor solutions since due to InSufficient Number of 
Indicators per Construct: https://davidakenny.net/cm/identify_formal.htm

#### Combined Sample (UA2 and UMGC1) 1-factor EFA of SRL Assessment (4 scales)
Although the RMSEA has a good value, the TLI and RMSR suggest a bad fit.  
```{r}
EFA_SRL1 <- fa(global_ua2umgc1[,c(3:6)], nfactors=1, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA_SRL1,cut = 0.2, sort=TRUE)
```

#### Combined Sample (UA2 and UMGC1) 2-factor EFA of SRL Assessment (4 scales)
It is an over-identified model (the df is negative, and the fit is good)   
```{r}
EFA_SRL2 <- fa(global_ua2umgc1[,c(3:6)], nfactors=2, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA_SRL2, cut = 0.2, sort=TRUE)
```

```{r}
fa.diagram(EFA_SRL2, cut=0.2, 
           main= "2-factor EFA,SRL, 4 scales, UA2 and UMGC1")
```

#### UA2 Sample 1-factor EFA of SRL Assessment (4 scales)
Although the RMSEA has a goodish value, the TLI and RMSR suggest a bad fit.  
```{r}
EFA_SRL1ua2 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UA2",c(3:6)], 
      nfactors=1, rotate="oblimin", SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA_SRL1ua2,cutoff = 0.2, sort=TRUE)
```

####  UA2 Sample 2-factor EFA of SRL Assessment (4 scales)
It is an over-identified model (the df is negative, and the fit is good)   
```{r}
EFA_SRL2ua2 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UA2",c(3:6)], 
      nfactors=2, rotate="oblimin", SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA_SRL2ua2, cut = 0.2, sort=TRUE)
```

```{r}
fa.diagram(EFA_SRL2ua2, cut=0.2, 
           main= "2-factor EFA,SRL, 4 scales, UA2")
```

#### UMGC1 Sample 1-factor EFA of SRL Assessment (4 scales)
Although the RMSEA has a goodish value, the TLI and RMSR suggest a bad fit.  
```{r}
EFA_SRL1umgc1 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UMGC1",c(3:6)], 
      nfactors=1, rotate="oblimin", SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA_SRL1umgc1,cut = 0.2, sort=TRUE)
```

####  UMGC1 Sample 2-factor EFA of SRL Assessment (4 scales)
It is an over-identified model (the df is negative, and the fit is good)   
```{r}
EFA_SRL2umgc1 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UMGC1",c(3:6)], 
nfactors=2,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(EFA_SRL2umgc1,cut = 0.2, sort=TRUE)
```

```{r}
fa.diagram(EFA_SRL2umgc1, cut=0.2, 
           main= "2-factor EFA,SRL, 4 scales, UMGC1")
```

### Parallel Analyses of SRL Assessment with 14 subscales' scores as indicators. 
Planning, Monitoring, Evaluating, Mastery, Mindset, Anxiety, Environment, 
The subscales of Planning, Monitoring, Evaluating, Mastery, Mindset, Anxiety, 
Environment, Time, Understanding, Help-seeking, Self-Efficacy for Math, 
Self-Efficacy for Reading, Self-Efficacy for Writing, and Self-Efficacy for 
Online Learning. 
The model suggests a four-factor structure of the SRL Assessment, which 
corresponds to the theoretical model. 

#### Combined Sample (UA2 and UMGC1) Parallel Analysis of fourteen SRL subscales
Parallel analysis suggests 4-factor structure of SRL assessment made of 14 
subscales.
```{r}
fa.parallel(global_ua2umgc1[,c(7:20)],fa="fa",fm="ml",n.iter=1000,
  main="Parallel Analysis Scree plot for fourteen SRL subscales, UA2 and UMGC1")
```

#### UMGC1 Sample Parallel Analysis of fourteen SRL subscales
Parallel analysis suggests 4-factor structure of SRL assessment made of 14 
subscales.
```{r}
fa.parallel(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(7:20)],fm="ml",
          fa="fa",n.iter=1000,
          main="Parallel Analysis Scree plot for fourteen SRL subscales, UMGC1")
```

#### UA2 Sample Parallel Analysis of fourteen SRL subscales
Parallel analysis suggests 4-factor structure of SRL assessment made of 14 
subscales.
```{r}
fa.parallel(global_ua2umgc1[global_ua2umgc1$college=="UA2",c(7:20)],fa="fa",
                fm="ml",n.iter=1000,
            main="Parallel Analysis Scree plot for fourteen SRL subscales, UA2")
```

### Exploratory Factor Analyses (EFA) of SRL Assessment (14 subscales)
The 1-, 2-, 3-, and 9-factor models have a poor fit to the data. The 4-, 5-, 6-, 
7-, and 8-factor models have a good fit to the data.

#### Combined Sample (UA2 and UMGC1) 1-factor EFA of SRL Assessment (14 scales)
The model has a poor fit.  
```{r}
EFA1_SRL14 <- fa(global_ua2umgc1[,c(7:20)], nfactors=1, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA1_SRL14,cut = 0.2, sort=TRUE)
```
##### UA2 Sample 1-factor EFA of SRL Assessment (14 scales)
The model has a poor fit.  
```{r}
EFA1_SRL14ua2 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UA2",c(7:20)], 
      nfactors=1, rotate="oblimin", SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA1_SRL14ua2,cut = 0.2, sort=TRUE)
```

##### UMGC1 Sample 1-factor EFA of SRL Assessment (14 scales)
The model has a poor fit.  
```{r}
EFA1_SRL14umgc1 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UMGC1",
        c(7:20)],nfactors=1, rotate="oblimin", SMC=TRUE, 
        max.iter=1000, fm="ml", alpha=.05)
print(EFA1_SRL14umgc1,cut = 0.2, sort=TRUE)
```

#### Combined Sample (UA2 and UMGC1) 2-factor EFA of SRL Assessment (14 scales)
The model has a poor fit.  
```{r}
EFA2_SRL14 <- fa(global_ua2umgc1[,c(7:20)], nfactors=2, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA2_SRL14,cut = 0.2, sort=TRUE)
```
##### UA2 Sample 2-factor EFA of SRL Assessment (14 scales)
The model has a poor fit.  
```{r}
EFA2_SRL14ua2 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UA2",c(7:20)], 
      nfactors=2, rotate="oblimin", SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA2_SRL14ua2,cut = 0.2, sort=TRUE)
```

##### UMGC1 Sample 2-factor EFA of SRL Assessment (14 scales)
The model has a poor fit.  
```{r}
EFA2_SRL14umgc1 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UMGC1",
        c(7:20)],nfactors=2, rotate="oblimin", SMC=TRUE, 
        max.iter=1000, fm="ml", alpha=.05)
print(EFA2_SRL14umgc1,cut = 0.2, sort=TRUE)
```

#### Combined Sample (UA2 and UMGC1) 3-factor EFA of SRL Assessment (14 scales)
The model has a moderate fit.  
```{r}
EFA3_SRL14 <- fa(global_ua2umgc1[,c(7:20)], nfactors=3, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA3_SRL14,cut = 0.2, sort=TRUE)
```

##### UA2 Sample 3-factor EFA of SRL Assessment (14 scales)
The model has a moderate fit.  
```{r}
EFA3_SRL14ua2 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UA2",c(7:20)], 
      nfactors=3, rotate="oblimin", SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA3_SRL14ua2,cut = 0.2, sort=TRUE)
```

##### UMGC1 Sample 3-factor EFA of SRL Assessment (14 scales)
The model has a poor fit.  
```{r}
EFA3_SRL14umgc1 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UMGC1",
        c(7:20)],nfactors=3, rotate="oblimin", SMC=TRUE, 
        max.iter=1000, fm="ml", alpha=.05)
print(EFA3_SRL14umgc1,cut = 0.2, sort=TRUE)
```

#### Combined Sample (UA2 and UMGC1) 4-factor EFA of SRL Assessment (14 scales)
The model has a good fit.  
```{r}
EFA4_SRL14 <- fa(global_ua2umgc1[,c(7:20)], nfactors=4, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA4_SRL14,cut = 0.2, sort=TRUE)
```

##### UA2 Sample 4-factor EFA of SRL Assessment (14 scales)
The model has a good fit.  
```{r}
EFA4_SRL14ua2 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UA2",c(7:20)], 
      nfactors=4, rotate="oblimin", SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA4_SRL14ua2,cut = 0.2, sort=TRUE)
```

```{r}
fa.diagram(EFA4_SRL14ua2, cut=0.2, main= "4-factor EFA,SRL, 14 subscales, UA2")
```

##### UMGC1 Sample 4-factor EFA of SRL Assessment (14 scales)
The model has an acceptable fit.  
```{r}
EFA4_SRL14umgc1 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UMGC1",
        c(7:20)],nfactors=4, rotate="oblimin", SMC=TRUE, 
        max.iter=1000, fm="ml", alpha=.05)
print(EFA4_SRL14umgc1,cut = 0.2, sort=TRUE)
```

#### Combined Sample (UA2 and UMGC1) 5-factor EFA of SRL Assessment (14 scales)
The model has a good fit.  
```{r}
EFA5_SRL14 <- fa(global_ua2umgc1[,c(7:20)], nfactors=5, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA5_SRL14,cut = 0.2, sort=TRUE)
```

```{r}
fa.diagram(EFA5_SRL14, cut=0.2, 
           main= "5-factor EFA,SRL, 14 subscales, UA2 and UMGC1")
```


##### UA2 Sample 5-factor EFA of SRL Assessment (14 scales)
The model has a good fit.  
```{r}
EFA5_SRL14ua2 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UA2",c(7:20)], 
      nfactors=5, rotate="oblimin", SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA5_SRL14ua2,cut = 0.2, sort=TRUE)
```

##### UMGC1 Sample 5-factor EFA of SRL Assessment (14 scales)
The model has a good fit.  
```{r}
EFA5_SRL14umgc1 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UMGC1",
        c(7:20)],nfactors=5, rotate="oblimin", SMC=TRUE, 
        max.iter=1000, fm="ml", alpha=.05)
print(EFA5_SRL14umgc1,cut = 0.2, sort=TRUE)
```

#### Combined Sample (UA2 and UMGC1) 6-factor EFA of SRL Assessment (14 scales)
The model has a good fit.  
```{r}
EFA6_SRL14 <- fa(global_ua2umgc1[,c(7:20)], nfactors=6, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA6_SRL14,cut = 0.2, sort=TRUE)
```

##### UA2 Sample 6-factor EFA of SRL Assessment (14 scales)
The model has a good fit.  
```{r}
EFA6_SRL14ua2 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UA2",c(7:20)], 
      nfactors=6, rotate="oblimin", SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA6_SRL14ua2,cut = 0.2, sort=TRUE)
```

##### UMGC1 Sample 6-factor EFA of SRL Assessment (14 scales)
The model has a good fit.  
```{r}
EFA6_SRL14umgc1 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UMGC1",
        c(7:20)],nfactors=6, rotate="oblimin", SMC=TRUE, 
        max.iter=1000, fm="ml", alpha=.05)
print(EFA6_SRL14umgc1,cut = 0.2, sort=TRUE)
```

#### Combined Sample (UA2 and UMGC1) 7-factor EFA of SRL Assessment (14 scales)
The model has a good fit.  
```{r}
EFA7_SRL14 <- fa(global_ua2umgc1[,c(7:20)], nfactors=7, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA7_SRL14,cut = 0.2, sort=TRUE)
```

##### UA2 Sample 7-factor EFA of SRL Assessment (14 scales)
The model has a good fit.  
```{r}
EFA7_SRL14ua2 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UA2",c(7:20)], 
      nfactors=7, rotate="oblimin", SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA7_SRL14ua2,cut = 0.2, sort=TRUE)
```

##### UMGC1 Sample 7-factor EFA of SRL Assessment (14 scales)
The model has a good fit.  
```{r}
EFA7_SRL14umgc1 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UMGC1",
        c(7:20)],nfactors=7, rotate="oblimin", SMC=TRUE, 
        max.iter=1000, fm="ml", alpha=.05)
print(EFA7_SRL14umgc1,cut = 0.2, sort=TRUE)
```

#### Combined Sample (UA2 and UMGC1) 8-factor EFA of SRL Assessment (14 scales)
The model has a good fit.  
```{r}
EFA8_SRL14 <- fa(global_ua2umgc1[,c(7:20)], nfactors=8, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA8_SRL14,cut = 0.2, sort=TRUE)
```

##### UA2 Sample 8-factor EFA of SRL Assessment (14 scales)
The model has a good fit.  
```{r}
EFA8_SRL14ua2 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UA2",c(7:20)], 
      nfactors=8, rotate="oblimin", SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA8_SRL14ua2,cut = 0.2, sort=TRUE)
```

##### UMGC1 Sample 8-factor EFA of SRL Assessment (14 scales)
The model has a good fit.  
```{r}
EFA8_SRL14umgc1 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UMGC1",
        c(7:20)],nfactors=8, rotate="oblimin", SMC=TRUE, 
        max.iter=1000, fm="ml", alpha=.05)
print(EFA8_SRL14umgc1,cut = 0.2, sort=TRUE)
```

#### Combined Sample (UA2 and UMGC1) 9-factor EFA of SRL Assessment (14 scales)
The model has a bad fit.  
```{r}
EFA9_SRL14 <- fa(global_ua2umgc1[,c(7:20)], nfactors=9, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA9_SRL14,cut = 0.2, sort=TRUE)
```

##### UA2 Sample 9-factor EFA of SRL Assessment (14 scales)
The model has a bad fit.  
```{r}
EFA9_SRL14ua2 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UA2",c(7:20)], 
      nfactors=9, rotate="oblimin", SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(EFA9_SRL14ua2,cut = 0.2, sort=TRUE)
```

##### UMGC1 Sample 9-factor EFA of SRL Assessment (14 scales)
The model has a bad fit. 
```{r}
EFA9_SRL14umgc1 <- fa(global_ua2umgc1[global_ua2umgc1$college == "UMGC1",
        c(7:20)],nfactors=9, rotate="oblimin", SMC=TRUE, 
        max.iter=1000, fm="ml", alpha=.05)
print(EFA9_SRL14umgc1,cut = 0.2, sort=TRUE)
```

## CFA 1

### Specify the 4-factor CFA model 1
```{r}
CFA_SRL4f<- 'srl_motivation =~ srl_mastery_orientation +srl_mindset +srl_anxiety
srl_metacognition =~ srl_planning + srl_monitoring + srl_evaluation
srl_strategies =~ srl_managing_environment + srl_managing_time +
                srl_understanding + srl_help_seeking
srl_selfefficacy =~ srl_self_efficacy_for_mathematics2 +                                                                         srl_selfefficacy_for_online_learning + srl_selfefficacy_for_reading + 
          srl_selfefficacy_for_writing
srl_metacognition~~srl_motivation
srl_metacognition~~srl_strategies
srl_metacognition~~srl_selfefficacy
srl_motivation~~srl_strategies
srl_motivation~~srl_selfefficacy
srl_strategies~~srl_selfefficacy'
```

### Run the CFA model, Combined Sample (UA2 and UMGC1)
The model has a poor fit
```{r}
CFA_SRL4f_ua2umgc1_fit<-cfa(CFA_SRL4f,
                data=global_ua2umgc1[,c(7:20)],std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_ua2umgc1_fit, standardized=TRUE, fit.measures = TRUE)
```
```{r}
semPaths(CFA_SRL4f_ua2umgc1_fit,"std")
```


### Run the CFA model, UA2 Sample
The model has a poor fit
```{r}
CFA_SRL4f_ua2_fit<-cfa(CFA_SRL4f,
      data=global_ua2umgc1[global_ua2umgc1$college == "UA2",c(7:20)],
      std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_ua2_fit, standardized=TRUE, fit.measures = TRUE)
```

```{r}
semPaths(CFA_SRL4f_ua2_fit,"std")
```

### Run the CFA model, UMGC1 Sample
The model has a poor fit
```{r}
CFA_SRL4f_umgc1_fit<-cfa(CFA_SRL4f,
      data=global_ua2umgc1[global_ua2umgc1$college == "UMGC1",c(7:20)],
      std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_umgc1_fit, standardized=TRUE, fit.measures = TRUE)
```

```{r}
semPaths(CFA_SRL4f_umgc1_fit,"std")
```

#### Request Modification Indecies for combined sample CFA
```{r}
modindices(CFA_SRL4f_ua2umgc1_fit, sort = TRUE, maximum.number = 5)
```

#### Request Modification Indecies for UA2 sample CFA
```{r}
modindices(CFA_SRL4f_ua2_fit, sort = TRUE, maximum.number = 5)
```

#### Request Modification Indecies for UMGC1 sample CFA
```{r}
modindices(CFA_SRL4f_umgc1_fit, sort = TRUE, maximum.number = 5)
```
## CFA 2

Two sets of modification indecies suggest to correlate move the srl_anxiety to 
srl_metacognition factor

### Specify a modified 4-factor CFA model 2
move the srl_anxiety to srl_metacognition factor
```{r}
CFA_SRL4f_2<- 'srl_motivation =~ srl_mastery_orientation +srl_mindset 
srl_metacognition =~ srl_planning + srl_monitoring + srl_evaluation +srl_anxiety
srl_strategies =~ srl_managing_environment + srl_managing_time +
                srl_understanding + srl_help_seeking
srl_selfefficacy =~ srl_self_efficacy_for_mathematics2 +                                                                         srl_selfefficacy_for_online_learning + srl_selfefficacy_for_reading + 
            srl_selfefficacy_for_writing
srl_metacognition~~srl_motivation
srl_metacognition~~srl_strategies
srl_metacognition~~srl_selfefficacy
srl_motivation~~srl_strategies
srl_motivation~~srl_selfefficacy
srl_strategies~~srl_selfefficacy'
```

### Run the CFA model, Combined Sample (UA2 and UMGC1)
The model has a poor fit
```{r}
CFA_SRL4f_ua2umgc1_fit2<-cfa(CFA_SRL4f_2,
                data=global_ua2umgc1[,c(7:20)],std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_ua2umgc1_fit2, standardized=TRUE, fit.measures = TRUE)
```

```{r}
semPaths(CFA_SRL4f_ua2umgc1_fit2,"std")
```

#### Request Modification Indecies for the combined sample CFA
```{r}
modindices(CFA_SRL4f_ua2umgc1_fit2, sort = TRUE, maximum.number = 3)
```

### Run the CFA model, UA2 Sample
The model has a poor fit
```{r}
CFA_SRL4f_ua2_fit2<-cfa(CFA_SRL4f_2,
      data=global_ua2umgc1[global_ua2umgc1$college == "UA2",c(7:20)],
      std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_ua2_fit2, standardized=TRUE, fit.measures = TRUE)
```

```{r}
semPaths(CFA_SRL4f_ua2_fit2,"std")
```
#### Request Modification Indecies for the UA2 sample CFA
```{r}
modindices(CFA_SRL4f_ua2_fit2, sort = TRUE, maximum.number = 3)
```

### Run the CFA model, UMGC1 Sample
The model has a poor fit
```{r}
CFA_SRL4f_umgc1_fit2<-cfa(CFA_SRL4f_2,
      data=global_ua2umgc1[global_ua2umgc1$college == "UMGC1",c(7:20)],
      std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_umgc1_fit2, standardized=TRUE, fit.measures = TRUE)
```

```{r}
semPaths(CFA_SRL4f_umgc1_fit2,"std")
```

#### Request Modification Indecies for the UA2 sample CFA
```{r}
modindices(CFA_SRL4f_umgc1_fit2, sort = TRUE, maximum.number = 3)
```
## CFA 3

All three sets of modification indices suggest to move srl_anxiety to	
srl_selfefficacy factor

### Specify a modified 4-factor CFA model 3
```{r}
CFA_SRL4f_3<- 'srl_motivation =~ srl_mastery_orientation +srl_mindset 
srl_metacognition =~ srl_planning + srl_monitoring + srl_evaluation
srl_strategies =~ srl_managing_environment + srl_managing_time +
                srl_understanding + srl_help_seeking
srl_selfefficacy =~ srl_self_efficacy_for_mathematics2 + srl_anxiety+                                                             srl_selfefficacy_for_online_learning + srl_selfefficacy_for_reading + 
            srl_selfefficacy_for_writing
srl_metacognition~~srl_motivation
srl_metacognition~~srl_strategies
srl_metacognition~~srl_selfefficacy
srl_motivation~~srl_strategies
srl_motivation~~srl_selfefficacy
srl_strategies~~srl_selfefficacy'
```

### Run the CFA model, Combined Sample (UA2 and UMGC1)
The model has a poor fit
```{r}
CFA_SRL4f_ua2umgc1_fit3<-cfa(CFA_SRL4f_3,
                data=global_ua2umgc1[,c(7:20)],std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_ua2umgc1_fit3, standardized=TRUE, fit.measures = TRUE)
```

```{r}
semPaths(CFA_SRL4f_ua2umgc1_fit3,"std")
```

#### Request Modification Indecies for the combined sample CFA
```{r}
modindices(CFA_SRL4f_ua2umgc1_fit3, sort = TRUE, maximum.number = 5)
```

### Run the CFA model, UA2 Sample
The model has a poor fit
```{r}
CFA_SRL4f_ua2_fit3<-cfa(CFA_SRL4f_3,
                data=global_ua2umgc1[global_ua2umgc1$college == "UA2",c(7:20)],
                std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_ua2_fit3, standardized=TRUE, fit.measures = TRUE)
```
CFA_SRL4f_ua2umgc1_fit3
```{r}
semPaths(CFA_SRL4f_ua2_fit3,"std")
```

#### Request Modification Indecies for the combined sample CFA
```{r}
modindices(CFA_SRL4f_ua2_fit3, sort = TRUE, maximum.number = 5)
```

### Run the CFA model, UMGC1 Sample
The model has a poor fit
```{r}
CFA_SRL4f_umgc1_fit3<-cfa(CFA_SRL4f_3,
              data=global_ua2umgc1[global_ua2umgc1$college == "UMGC1",c(7:20)],
                std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_umgc1_fit3, standardized=TRUE, fit.measures = TRUE)
```

```{r}
semPaths(CFA_SRL4f_umgc1_fit3,"std")
```

#### Request Modification Indecies for the combined sample CFA
```{r}
modindices(CFA_SRL4f_umgc1_fit3, sort = TRUE, maximum.number = 5)
```

## CFA 4

All three sets of modification indices suggest to correlate the indicators of
srl_managing_environment and srl_managing_time.

### Specify a modified 4-factor CFA model 4

```{r}
CFA_SRL4f_4<- 'srl_motivation =~ srl_mastery_orientation +srl_mindset 
srl_metacognition =~ srl_planning + srl_monitoring + srl_evaluation
srl_strategies =~ srl_managing_environment + srl_managing_time +
                srl_understanding + srl_help_seeking
srl_selfefficacy =~ srl_self_efficacy_for_mathematics2 + srl_anxiety+                                                             srl_selfefficacy_for_online_learning + srl_selfefficacy_for_reading + 
            srl_selfefficacy_for_writing
srl_metacognition~~srl_motivation
srl_metacognition~~srl_strategies
srl_metacognition~~srl_selfefficacy
srl_motivation~~srl_strategies
srl_motivation~~srl_selfefficacy
srl_strategies~~srl_selfefficacy
srl_managing_environment~~srl_managing_time'
```

### Run the CFA model, Combined Sample (UA2 and UMGC1)
The model has a poor fit
```{r}
CFA_SRL4f_ua2umgc1_fit4<-cfa(CFA_SRL4f_4,
                data=global_ua2umgc1[,c(7:20)],std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_ua2umgc1_fit4, standardized=TRUE, fit.measures = TRUE)
```

```{r}
semPaths(CFA_SRL4f_ua2umgc1_fit4,"std")
```

#### Request Modification Indecies for the combined sample CFA
```{r}
modindices(CFA_SRL4f_ua2umgc1_fit4, sort = TRUE, maximum.number = 5)
```

### Run the CFA model, UA2 Sample
The model has a poor fit
```{r}
CFA_SRL4f_ua2_fit4<-cfa(CFA_SRL4f_4,
                data=global_ua2umgc1[global_ua2umgc1$college == "UA2",c(7:20)],
                std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_ua2_fit4, standardized=TRUE, fit.measures = TRUE)
```
CFA_SRL4f_ua2umgc1_fit4
```{r}
semPaths(CFA_SRL4f_ua2_fit4,"std")
```

#### Request Modification Indecies for the combined sample CFA
```{r}
modindices(CFA_SRL4f_ua2_fit4, sort = TRUE, maximum.number = 5)
```

### Run the CFA model, UMGC1 Sample
The model has a poor fit
```{r}
CFA_SRL4f_umgc1_fit4<-cfa(CFA_SRL4f_4,
              data=global_ua2umgc1[global_ua2umgc1$college == "UMGC1",c(7:20)],
                std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_umgc1_fit4, standardized=TRUE, fit.measures = TRUE)
```

```{r}
semPaths(CFA_SRL4f_umgc1_fit4,"std")
```

#### Request Modification Indecies for the combined sample CFA
```{r}
modindices(CFA_SRL4f_umgc1_fit4, sort = TRUE, maximum.number = 5)
```
## CFA 5

All three sets of modification indices suggest to correlate the indicators of
srl_anxiety and srl_self_efficacy_for_mathematics2

### Specify a modified 4-factor CFA model 5

```{r}
CFA_SRL4f_5<- 'srl_motivation =~ srl_mastery_orientation +srl_mindset 
srl_metacognition =~ srl_planning + srl_monitoring + srl_evaluation
srl_strategies =~ srl_managing_environment + srl_managing_time +
                srl_understanding + srl_help_seeking
srl_selfefficacy =~ srl_self_efficacy_for_mathematics2 + srl_anxiety+                                                             srl_selfefficacy_for_online_learning + srl_selfefficacy_for_reading + 
            srl_selfefficacy_for_writing
srl_metacognition~~srl_motivation
srl_metacognition~~srl_strategies
srl_metacognition~~srl_selfefficacy
srl_motivation~~srl_strategies
srl_motivation~~srl_selfefficacy
srl_strategies~~srl_selfefficacy
srl_managing_environment~~srl_managing_time
srl_self_efficacy_for_mathematics2~~srl_anxiety'
```

### Run the CFA model, Combined Sample (UA2 and UMGC1)
The model has a poor fit
```{r}
CFA_SRL4f_ua2umgc1_fit5<-cfa(CFA_SRL4f_5,
                data=global_ua2umgc1[,c(7:20)],std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_ua2umgc1_fit5, standardized=TRUE, fit.measures = TRUE)
```

```{r}
semPaths(CFA_SRL4f_ua2umgc1_fit5,"std")
```

#### Request Modification Indecies for the combined sample CFA
```{r}
modindices(CFA_SRL4f_ua2umgc1_fit5, sort = TRUE, maximum.number = 5)
```

### Run the CFA model, UA2 Sample
The model has a poor fit
```{r}
CFA_SRL4f_ua2_fit5<-cfa(CFA_SRL4f_5,
                data=global_ua2umgc1[global_ua2umgc1$college == "UA2",c(7:20)],
                std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_ua2_fit5, standardized=TRUE, fit.measures = TRUE)
```
CFA_SRL4f_ua2umgc1_fit5
```{r}
semPaths(CFA_SRL4f_ua2_fit5,"std")
```

#### Request Modification Indecies for the combined sample CFA
```{r}
modindices(CFA_SRL4f_ua2_fit5, sort = TRUE, maximum.number = 5)
```

### Run the CFA model, UMGC1 Sample
The model has a poor fit
```{r}
CFA_SRL4f_umgc1_fit5<-cfa(CFA_SRL4f_5,
              data=global_ua2umgc1[global_ua2umgc1$college == "UMGC1",c(7:20)],
                std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_umgc1_fit5, standardized=TRUE, fit.measures = TRUE)
```

```{r}
semPaths(CFA_SRL4f_umgc1_fit5,"std")
```

#### Request Modification Indecies for the combined sample CFA
```{r}
modindices(CFA_SRL4f_umgc1_fit5, sort = TRUE, maximum.number = 5)
```

## CFA 6

All three sets of modification indices suggest to correlate the indicators of
srl_selfefficacy_for_reading and srl_selfefficacy_for_writing

### Specify a modified 4-factor CFA model 6

```{r}
CFA_SRL4f_6<- 'srl_motivation =~ srl_mastery_orientation +srl_mindset 
srl_metacognition =~ srl_planning + srl_monitoring + srl_evaluation
srl_strategies =~ srl_managing_environment + srl_managing_time +
                srl_understanding + srl_help_seeking
srl_selfefficacy =~ srl_self_efficacy_for_mathematics2 + srl_anxiety+                                                             srl_selfefficacy_for_online_learning + srl_selfefficacy_for_reading + 
            srl_selfefficacy_for_writing
srl_metacognition~~srl_motivation
srl_metacognition~~srl_strategies
srl_metacognition~~srl_selfefficacy
srl_motivation~~srl_strategies
srl_motivation~~srl_selfefficacy
srl_strategies~~srl_selfefficacy
srl_managing_environment~~srl_managing_time
srl_self_efficacy_for_mathematics2~~srl_anxiety
srl_selfefficacy_for_reading~~srl_selfefficacy_for_writing'
```

### Run the CFA model, Combined Sample (UA2 and UMGC1)
The model has a poor fit
```{r}
CFA_SRL4f_ua2umgc1_fit6<-cfa(CFA_SRL4f_6,
                data=global_ua2umgc1[,c(7:20)],std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_ua2umgc1_fit6, standardized=TRUE, fit.measures = TRUE)
```

```{r}
semPaths(CFA_SRL4f_ua2umgc1_fit6,"std")
```

#### Request Modification Indecies for the combined sample CFA
```{r}
modindices(CFA_SRL4f_ua2umgc1_fit6, sort = TRUE, maximum.number = 5)
```

### Run the CFA model, UA2 Sample
The model has a poor fit
```{r}
CFA_SRL4f_ua2_fit6<-cfa(CFA_SRL4f_6,
                data=global_ua2umgc1[global_ua2umgc1$college == "UA2",c(7:20)],
                std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_ua2_fit6, standardized=TRUE, fit.measures = TRUE)
```
CFA_SRL4f_ua2umgc1_fit6
```{r}
semPaths(CFA_SRL4f_ua2_fit6,"std")
```

#### Request Modification Indecies for the combined sample CFA
```{r}
modindices(CFA_SRL4f_ua2_fit6, sort = TRUE, maximum.number = 5)
```

### Run the CFA model, UMGC1 Sample
The model has a poor fit
```{r}
CFA_SRL4f_umgc1_fit6<-cfa(CFA_SRL4f_6,
              data=global_ua2umgc1[global_ua2umgc1$college == "UMGC1",c(7:20)],
                std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_umgc1_fit6, standardized=TRUE, fit.measures = TRUE)
```

```{r}
semPaths(CFA_SRL4f_umgc1_fit6,"std")
```

#### Request Modification Indecies for the combined sample CFA
```{r}
modindices(CFA_SRL4f_umgc1_fit6, sort = TRUE, maximum.number = 5)
```
## CFA 7

All three sets of modification indices suggest to correlate the indicators of
srl_planning and srl_evaluation

### Specify a modified 4-factor CFA model 7

```{r}
CFA_SRL4f_7<- 'srl_motivation =~ srl_mastery_orientation +srl_mindset 
srl_metacognition =~ srl_planning + srl_monitoring + srl_evaluation
srl_strategies =~ srl_managing_environment + srl_managing_time +
                srl_understanding + srl_help_seeking
srl_selfefficacy =~ srl_self_efficacy_for_mathematics2 + srl_anxiety+                                                             srl_selfefficacy_for_online_learning + srl_selfefficacy_for_reading + 
            srl_selfefficacy_for_writing
srl_metacognition~~srl_motivation
srl_metacognition~~srl_strategies
srl_metacognition~~srl_selfefficacy
srl_motivation~~srl_strategies
srl_motivation~~srl_selfefficacy
srl_strategies~~srl_selfefficacy
srl_managing_environment~~srl_managing_time
srl_self_efficacy_for_mathematics2~~srl_anxiety
srl_selfefficacy_for_reading~~srl_selfefficacy_for_writing
srl_planning~~srl_evaluation'
```

### Run the CFA model, Combined Sample (UA2 and UMGC1)
The model has a poor fit
```{r}
CFA_SRL4f_ua2umgc1_fit7<-cfa(CFA_SRL4f_7,
                data=global_ua2umgc1[,c(7:20)],std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_ua2umgc1_fit7, standardized=TRUE, fit.measures = TRUE)
```

```{r}
semPaths(CFA_SRL4f_ua2umgc1_fit7,"std")
```

#### Request Modification Indecies for the combined sample CFA
```{r}
modindices(CFA_SRL4f_ua2umgc1_fit7, sort = TRUE, maximum.number = 5)
```

### Run the CFA model, UA2 Sample
The model has a poor fit
```{r}
CFA_SRL4f_ua2_fit7<-cfa(CFA_SRL4f_7,
                data=global_ua2umgc1[global_ua2umgc1$college == "UA2",c(7:20)],
                std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_ua2_fit7, standardized=TRUE, fit.measures = TRUE)
```
CFA_SRL4f_ua2umgc1_fit7
```{r}
semPaths(CFA_SRL4f_ua2_fit7,"std")
```

#### Request Modification Indecies for the combined sample CFA
```{r}
modindices(CFA_SRL4f_ua2_fit7, sort = TRUE, maximum.number = 5)
```

### Run the CFA model, UMGC1 Sample
The model has a poor fit
```{r}
CFA_SRL4f_umgc1_fit7<-cfa(CFA_SRL4f_7,
              data=global_ua2umgc1[global_ua2umgc1$college == "UMGC1",c(7:20)],
                std.lv=TRUE, orthogonal=FALSE)
summary(CFA_SRL4f_umgc1_fit7, standardized=TRUE, fit.measures = TRUE)
```

```{r}
semPaths(CFA_SRL4f_umgc1_fit7,"std")
```

#### Request Modification Indecies for the combined sample CFA
```{r}
modindices(CFA_SRL4f_umgc1_fit7, sort = TRUE, maximum.number = 5)
```


#Reference
Furr, R. M. (2014). Scale construction and psychometrics for social and 
personality psychology.Thousand Oaks, CA: SAGE.doi:10.4135/9781446287866




