---
title: "DAACS_UA2_UMGC1_Total Scores-Histograms-Boxplots-Error bars"
author: "Oxana Rosca"
date: "2023-01-06"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(psych)
```

Load the data file
```{r}
global_ua2umgc1 <- readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/global_ua2umgc1.rds")
```

Total Number of Participants and Demographics or how many participants and 
variables you have:
```{r}
dim(global_ua2umgc1)
```

*Verify the File*
Test for duplicate values DAACS_ID
Frequencies: How many of non-duplicated IDs?
```{r}
table(duplicated(global_ua2umgc1$DAACS_ID))
```
Test for empty rows:
```{r}
global_ua2umgc1_Check<-
  global_ua2umgc1[rowSums(is.na(global_ua2umgc1))!=ncol(global_ua2umgc1),]
```
Comparing the # of cases, there are no empty rows

See the minimum time taken for every assessment IN MINUTES
```{r}
min(global_ua2umgc1$readTime, na.rm = TRUE)
min(global_ua2umgc1$mathTime, na.rm = TRUE)
min(global_ua2umgc1$srlTime, na.rm = TRUE)
min(global_ua2umgc1$writeTime, na.rm = TRUE)
```
Check that only the first attempts are subset:
```{r}
max(global_ua2umgc1$read_attempt, na.rm = TRUE)
max(global_ua2umgc1$math_attempt, na.rm = TRUE)
max(global_ua2umgc1$srl_attempt, na.rm = TRUE)
max(global_ua2umgc1$write_attempt, na.rm = TRUE)
```

*Descriptives*
for the SRL scores for the combined sample (ua2 and umgc1)

```{r}
describe(global_ua2umgc1[,c(3:6)])
```

for the SRL scores by the college variable
```{r}
describeBy(global_ua2umgc1[,c(3:6)],global_ua2umgc1$college)
```

DAACS scores for the combined sample (ua2 and umgc1)
```{r}
describe(global_ua2umgc1[,c(39,49,236)])
```


DAACS scores by the college variable
```{r}
describeBy(global_ua2umgc1[,c(39,49,236)],global_ua2umgc1$college)
```

*Error Bars*
Graph the data with error bars for each variable

```{r}
error.bars(global_ua2umgc1 [,c(3:6)],density = 0,ylab= "Mean Score",
      xlab="SRL Scales",main ="95% CIs for Means on SRL Scales, UA2 and UMGC1")
```

```{r}
error.bars(global_ua2umgc1 [,c(39,49,236)],density = 0,ylab= "Mean Score",
      xlab="SRL Scales",main ="95% CIs for Means on DAACS scales,UA2 and UMGC1")
```

```{r}
error.bars(global_ua2umgc1 [c(1:1062),c(3:6)],density = 0,ylab= "Mean Score",
      xlab="SRL Scales",main ="95% CIs for Means on SRL Scales, UMGC1")
```

```{r}
error.bars(global_ua2umgc1 [c(1:1062),c(39,49,236)],density = 0,ylab= "Mean Score",
      xlab="SRL Scales",main ="95% CIs for Means on DAACS scales, UMGC1")
```


```{r}
error.bars(global_ua2umgc1 [c(1063:2208),c(3:6)],density = 0,ylab= "Mean Score",
      xlab="SRL Scales",main ="95% CIs for Means on SRL Scales, UA2")
```

```{r}
error.bars(global_ua2umgc1 [c(1063:2208),c(39,49,236)],density = 0,ylab= "Mean Score",
      xlab="DAACS Scales",main ="95% CIs for Means on DAACS Scales, UA2")
```


```{r}
error.bars(global_ua2umgc1 [,c(3)],density=-1,ylim= c(2.4,2.6),ann=FALSE,
      xlab="SRL Scales",main ="95% CIs for Means on SRL Scales, UA2 and UMGC1",
      group = global_ua2umgc1$college)
```
*Boxplots*

```{r}
boxplot(global_ua2umgc1 [,c(3:6)])
```


```{r}
boxplot(global_ua2umgc1$srl_strategies~global_ua2umgc1$college, notch=TRUE)
```
Since the notches of two plots do not overlap, there is a ‘strong evidence’ that 
the two medians differ (Chambers et al, 1983, p. 62).
```{r}
boxplot(global_ua2umgc1$srl_strategies~global_ua2umgc1$college, notch=TRUE, plot=FALSE)
```


```{r}
boxplot(global_ua2umgc1 [,c(39,49,236)])
```

```{r}
boxplot(global_ua2umgc1$mathTotal,global_ua2umgc1$college, notch=TRUE)
```
Since the notches of two plots do not overlap, there is a ‘strong evidence’ that 
the two medians differ (Chambers et al, 1983, p. 62).
```{r}
boxplot(global_ua2umgc1$mathTotal,global_ua2umgc1$college, notch=TRUE,plot=FALSE)
```


```{r}
stem(global_ua2umgc1$mathTotal)
```

```{r}
stem(global_ua2umgc1$readTotal)
```

```{r}
stem(global_ua2umgc1$writeTotal)
```

```{r}
stem(global_ua2umgc1$srlTotal)
```