---
title: "DAACS_SRL_DataOrganizing_UMGC1_Sep16_2022_OR"
author: "Oxana Rosca"
date: "2022-12-02"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(maditr)
library(ggplot2)
```

#setwd("D:OneDrive - University at Albany - SUNY/WorkDirectory")

Load data files
```{r}
#load("data_export/DAACS-Results-umgc_2022-09-16.rda")
load("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/DAACS-Results-umgc_2022-09-16.rda")
```

*Duplicates*
Test for duplicate values in srl.items.response
Frequencies: How many of non-duplicated IDs?
```{r}
table(duplicated(daacs$DAACS_ID))
```

```{r}
table(duplicated(srl.items.score$DAACS_ID))
```
There are 30 duplicated DAACS_ID in srl.items.score (they are the second 
attempts)

*Attempts*
How many of each number of attempts?
```{r}
table(srl.items.score$attempt, useNA = 'ifany') %>% 
  print() %>% prop.table()* 100
```
Select the first attempts only
```{r}
umgc1srl.items.score <- srl.items.score [srl.items.score$attempt == "1",]
```

*Save the New File*
Adding a variable of college and saving the new data file:
```{r}
umgc1srl.items.score$college <- 'UMGC1'
saveRDS(umgc1srl.items.score, file = 'umgc1srl.items.score.rds')
write.table(umgc1srl.items.score, 'umgc1srl.items.score.csv', sep=',')
```

*Merge*
Using all.y = TRUE so that we use only students who took the SRL survey. These 
are all newly enrolled students' data on Sep 16th, 2022 (Removing all students 
that did not take SRL survey).
```{r}
umgc1SRLDaacs<-merge(daacs,umgc1srl.items.score[,c(1,69)],by='DAACS_ID',all.y=TRUE)
```

*Test Time*
Calculate test time IN MINUTES per student:
```{r}
umgc1SRLDaacs$srlTime= (umgc1SRLDaacs$srlCompletionDate - 
                            umgc1SRLDaacs$srlStartDate)/60
```

To remove the non-numeric substring "sec" from the values of srlTime
```{r}
time_var_temp <- 
lapply(umgc1SRLDaacs[63],function(x)as.numeric(sub("\\s+\\D+$","",x)))
time_var_temp<-as.data.frame(time_var_temp)
View(time_var_temp)
umgc1SRLDaacs$srlTime<-time_var_temp$srlTime
View(umgc1SRLDaacs)
```

see the minimum value IN MINUTES
```{r}
min(umgc1SRLDaacs$srlTime)
```

How many students took less than 2 minutes?
```{r}
nrow(umgc1SRLDaacs[umgc1SRLDaacs$srlTime <= 2,])
```
I do not define neither remove speedy students.


*Total Score*
Histogram of the srl scores in points
```{r}
#library(ggplot2)
ggplot(umgc1SRLDaacs, aes(x = srlTotal)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('SRL Total') +   
                    ylab('Number of Students')
```
Cut the variable of scores into three categories of dots
```{r}
umgc1SRLDaacs$srlTotalDots <- cut(umgc1SRLDaacs$srlTotal,
                              breaks=c(0, 2, 3, 4),labels=c('1', '2', '3'))
```

To build a bar-plot of the reading scores in dots

```{r}
table(umgc1SRLDaacs$srlTotalDots)
```

```{r}
barplot(table(umgc1SRLDaacs$srlTotalDots),
        main="UMGC1 SRL Total Score in Dots",
          xlab="SRL Total in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```



```{r}
ggplot(umgc1SRLDaacs, aes(x = srl_strategies)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('SRL strategies') +   
                    ylab('Number of Students')
```

```{r}
umgc1SRLDaacs$srlStrategieslDots <- cut(umgc1SRLDaacs$srl_strategies,
                              breaks=c(0, 2, 3, 4),labels=c('1', '2', '3'))
table(umgc1SRLDaacs$srlStrategieslDots)
barplot(table(umgc1SRLDaacs$srlStrategieslDots),
        main="umgc1 SRL strategies in Dots",
          xlab="SRL strategies in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```

```{r}
ggplot(umgc1SRLDaacs, aes(x = srl_motivation)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('SRL motivation') +   
                    ylab('Number of Students')
```

```{r}
umgc1SRLDaacs$srlmotivationlDots <- cut(umgc1SRLDaacs$srl_motivation,
                              breaks=c(0, 2, 3, 4),labels=c('1', '2', '3'))
table(umgc1SRLDaacs$srlmotivationlDots)
barplot(table(umgc1SRLDaacs$srlmotivationlDots),
        main="umgc1 SRL motivation in Dots",
          xlab="SRL motivation in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```


```{r}
ggplot(umgc1SRLDaacs, aes(x = srl_metacognition)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('SRL metacognition') +   
                    ylab('Number of Students')
```

```{r}
umgc1SRLDaacs$srlmetacognitionlDots <- cut(umgc1SRLDaacs$srl_metacognition,
                              breaks=c(0, 2, 3, 4),labels=c('1', '2', '3'))
table(umgc1SRLDaacs$srlmetacognitionlDots)
barplot(table(umgc1SRLDaacs$srlmetacognitionlDots),
        main="umgc1 SRL metacognition in Dots",
          xlab="SRL metacognition in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```


```{r}
ggplot(umgc1SRLDaacs, aes(x = srl_selfefficacy)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('SRL selfefficacy') +   
                    ylab('Number of Students')
```

```{r}
umgc1SRLDaacs$srlselfefficacylDots <- cut(umgc1SRLDaacs$srl_selfefficacy,
                              breaks=c(0, 2, 3, 4),labels=c('1', '2', '3'))
table(umgc1SRLDaacs$srlselfefficacylDots)
barplot(table(umgc1SRLDaacs$srlselfefficacylDots),
        main="umgc1 SRL selfefficacy in Dots",
          xlab="SRL selfefficacy in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```


```{r}
ggplot(umgc1SRLDaacs, aes(x = srl_managing_time)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('SRL managing_time') +   
                    ylab('Number of Students')
```

```{r}
umgc1SRLDaacs$srlmanaging_timelDots <- cut(umgc1SRLDaacs$srl_managing_time,
                              breaks=c(0, 2, 3, 4),labels=c('1', '2', '3'))
table(umgc1SRLDaacs$srlmanaging_timelDots)
barplot(table(umgc1SRLDaacs$srlmanaging_timelDots),
        main="umgc1 SRL managing_time in Dots",
          xlab="SRL managing_time in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```


```{r}
ggplot(umgc1SRLDaacs, aes(x = srl_help_seeking)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('SRL help_seeking') +   
                    ylab('Number of Students')
```

```{r}
umgc1SRLDaacs$srlhelp_seekinglDots <- cut(umgc1SRLDaacs$srl_help_seeking,
                              breaks=c(0, 2, 3, 4),labels=c('1', '2', '3'))
table(umgc1SRLDaacs$srlhelp_seekinglDots)
barplot(table(umgc1SRLDaacs$srlhelp_seekinglDots),
        main="umgc1 SRL help_seeking in Dots",
          xlab="SRL help_seeking in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```


```{r}
ggplot(umgc1SRLDaacs, aes(x = srl_managing_environment)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('SRL managing_environment') +   
                    ylab('Number of Students')
```

```{r}
umgc1SRLDaacs$srlmanaging_environmentlDots <- cut(umgc1SRLDaacs$srl_managing_environment,
                              breaks=c(0, 2, 3, 4),labels=c('1', '2', '3'))
table(umgc1SRLDaacs$srlmanaging_environmentlDots)
barplot(table(umgc1SRLDaacs$srlmanaging_environmentlDots),
        main="umgc1 SRL managing_environment in Dots",
          xlab="SRL managing_environment in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```


```{r}
ggplot(umgc1SRLDaacs, aes(x = srl_understanding)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('SRL understanding') +   
                    ylab('Number of Students')
```

```{r}
umgc1SRLDaacs$srlunderstandinglDots <- cut(umgc1SRLDaacs$srl_understanding,
                              breaks=c(0, 2, 3, 4),labels=c('1', '2', '3'))
table(umgc1SRLDaacs$srlunderstandinglDots)
barplot(table(umgc1SRLDaacs$srlunderstandinglDots),
        main="umgc1 SRL understanding in Dots",
          xlab="SRL understanding in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```


```{r}
ggplot(umgc1SRLDaacs, aes(x = srl_anxiety)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('SRL anxiety') +   
                    ylab('Number of Students')
```

```{r}
umgc1SRLDaacs$srlanxietylDots <- cut(umgc1SRLDaacs$srl_anxiety,
                              breaks=c(0, 2, 3, 4),labels=c('1', '2', '3'))
table(umgc1SRLDaacs$srlanxietylDots)
barplot(table(umgc1SRLDaacs$srlanxietylDots),
        main="umgc1 SRL anxiety in Dots",
          xlab="SRL anxiety in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```


```{r}
ggplot(umgc1SRLDaacs, aes(x = srl_mastery_orientation)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('SRL mastery_orientation') +   
                    ylab('Number of Students')
```

```{r}
umgc1SRLDaacs$srlmastery_orientationlDots <- cut(umgc1SRLDaacs$srl_mastery_orientation,
                              breaks=c(0, 2, 3, 4),labels=c('1', '2', '3'))
table(umgc1SRLDaacs$srlmastery_orientationlDots)
barplot(table(umgc1SRLDaacs$srlmastery_orientationlDots),
        main="umgc1 SRL mastery_orientation in Dots",
          xlab="SRL mastery_orientation in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```


```{r}
ggplot(umgc1SRLDaacs, aes(x = srl_mindset)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('SRL mindset') +   
                    ylab('Number of Students')
```

```{r}
umgc1SRLDaacs$srlmindsetlDots <- cut(umgc1SRLDaacs$srl_mindset,
                              breaks=c(0, 2, 3, 4),labels=c('1', '2', '3'))
table(umgc1SRLDaacs$srlmindsetlDots)
barplot(table(umgc1SRLDaacs$srlmindsetlDots),
        main="umgc1 SRL mindset in Dots",
          xlab="SRL mindset in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```


```{r}
ggplot(umgc1SRLDaacs, aes(x = srl_evaluation)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('SRL evaluation') +   
                    ylab('Number of Students')
```

```{r}
umgc1SRLDaacs$srlevaluationlDots <- cut(umgc1SRLDaacs$srl_evaluation,
                              breaks=c(0, 2, 3, 4),labels=c('1', '2', '3'))
table(umgc1SRLDaacs$srlevaluationlDots)
barplot(table(umgc1SRLDaacs$srlevaluationlDots),
        main="umgc1 SRL evaluation in Dots",
          xlab="SRL evaluation in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```


```{r}
ggplot(umgc1SRLDaacs, aes(x = srl_monitoring)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('SRL monitoring') +   
                    ylab('Number of Students')
```

```{r}
umgc1SRLDaacs$srlmonitoringlDots <- cut(umgc1SRLDaacs$srl_monitoring,
                              breaks=c(0, 2, 3, 4),labels=c('1', '2', '3'))
table(umgc1SRLDaacs$srlmonitoringlDots)
barplot(table(umgc1SRLDaacs$srlmonitoringlDots),
        main="umgc1 SRL monitoring in Dots",
          xlab="SRL monitoring in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```


```{r}
ggplot(umgc1SRLDaacs, aes(x = srl_planning)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('SRL planning') +   
                    ylab('Number of Students')
```

```{r}
umgc1SRLDaacs$srlplanninglDots <- cut(umgc1SRLDaacs$srl_planning,
                              breaks=c(0, 2, 3, 4),labels=c('1', '2', '3'))
table(umgc1SRLDaacs$srlplanninglDots)
barplot(table(umgc1SRLDaacs$srlplanninglDots),
        main="umgc1 SRL planning in Dots",
          xlab="SRL planning in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```


```{r}
ggplot(umgc1SRLDaacs, aes(x = srl_self_efficacy_for_mathematics2)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('SRL self_efficacy_for_mathematics') +   
                    ylab('Number of Students')
```

```{r}
umgc1SRLDaacs$srlself_efficacy_for_mathematics2lDots <- cut(umgc1SRLDaacs$srl_self_efficacy_for_mathematics2,
                              breaks=c(0, 2, 3, 4),labels=c('1', '2', '3'))
table(umgc1SRLDaacs$srlself_efficacy_for_mathematics2lDots)
barplot(table(umgc1SRLDaacs$srlself_efficacy_for_mathematics2lDots),
        main="umgc1 SRL self_efficacy_for_mathematics in Dots",
          xlab="SRL self_efficacy_for_mathematics in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```



```{r}
ggplot(umgc1SRLDaacs, aes(x = srl_selfefficacy_for_online_learning)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('SRL selfefficacy_for_online_learning') +   
                    ylab('Number of Students')
```

```{r}
umgc1SRLDaacs$srlselfefficacy_for_online_learninglDots <- cut(umgc1SRLDaacs$srl_selfefficacy_for_online_learning,
                              breaks=c(0, 2, 3, 4),labels=c('1', '2', '3'))
table(umgc1SRLDaacs$srlselfefficacy_for_online_learninglDots)
barplot(table(umgc1SRLDaacs$srlselfefficacy_for_online_learninglDots),
        main="umgc1 SRL selfefficacy_for_online_learning in Dots",
          xlab="SRL selfefficacy_for_online_learning in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```


```{r}
ggplot(umgc1SRLDaacs, aes(x = srl_selfefficacy_for_reading)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('SRL selfefficacy_for_reading') +   
                    ylab('Number of Students')
```

```{r}
umgc1SRLDaacs$srlselfefficacy_for_readinglDots <- cut(umgc1SRLDaacs$srl_selfefficacy_for_reading,
                              breaks=c(0, 2, 3, 4),labels=c('1', '2', '3'))
table(umgc1SRLDaacs$srlselfefficacy_for_readinglDots)
barplot(table(umgc1SRLDaacs$srlselfefficacy_for_readinglDots),
        main="umgc1 SRL selfefficacy_for_reading in Dots",
          xlab="SRL selfefficacy_for_reading in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```


```{r}
ggplot(umgc1SRLDaacs, aes(x = srl_selfefficacy_for_writing)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('SRL selfefficacy_for_writing') +   
                    ylab('Number of Students')
```

```{r}
umgc1SRLDaacs$srlselfefficacy_for_writinglDots <- cut(umgc1SRLDaacs$srl_selfefficacy_for_writing,
                              breaks=c(0, 2, 3, 4),labels=c('1', '2', '3'))
table(umgc1SRLDaacs$srlselfefficacy_for_writinglDots)
barplot(table(umgc1SRLDaacs$srlselfefficacy_for_writinglDots),
        main="umgc1 SRL selfefficacy_for_writing in Dots",
          xlab="SRL selfefficacy_for_writing in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```

To check if there are empty rows:
```{r}
umgc1SRLDaacs_Check<-
  umgc1SRLDaacs[rowSums(is.na(umgc1SRLDaacs))!=ncol(umgc1SRLDaacs),]
```
Comparing the # of cases in umgc1SRLDaacs and umgc1SRLDaacs_Check (which are 
equal), there are no empty rows in umgc1SRLDaacs.

*Save New File*

Adding a variable of college and saving the new data file:
```{r}
umgc1SRLDaacs$college <- 'UMGC1'
saveRDS(umgc1SRLDaacs, file = 'umgc1SRLDaacs.rds')
## to save the output as a comma-separated excel sheet
write.table(umgc1SRLDaacs, 'umgc1SRLDaacs.csv', sep=',')
```

