---
title: "Writing Subscales (Criteria) Scores, Correlations and Bar Graphs"
author: "Oxana Rosca"
date: "2023-01-23"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The Writing scale consists of 10 criteria. The rubric assigns them to 5 groups 
as follows: 
  Content includes Summary and Suggestions
  Organization	includes Structure and	Transitions
  Paragraphs includes	Focus on a Main Idea and	Cohesion
  Sentences	includes Correct and	Complex
  Conventions	includes Usage and	Punctuation
```{r}
library(psych)
```
  
Data file
```{r}
global_ua2umgc1 <- readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/global_ua2umgc1.rds")
```

# Sample Sizes
or how many students took writing assessment?
# Select the writing scores for UA2
```{r}
table(global_ua2umgc1$college,global_ua2umgc1$write_attempt)
writeUA2 <- global_ua2umgc1[global_ua2umgc1$college == "UA2",]
nrow(writeUA2[writeUA2$writeTotal != "NA",])
```


# See the total frequencies for each item
table(math.items$qid)
```{r}
table(global_ua2umgc1[global_ua2umgc1$college=="UA2", which(global_ua2umgc1$writeTotal>=0)])
```


# Correlations among Writing Subscales (Criteria) Scores

## UA2 Correlations among Writing Subscales (Criteria) Scores
```{r}
writeUA2<-global_ua2umgc1[global_ua2umgc1$college=="UA2",27:36]
rho <- lowerCor(writeUA2)
corPlot(rho, main = "Correlations among Writing Subscales, UA2")
```
### with p-values
All correlations greater than 0.11 are statistically significant
```{r}
#corr.test(writeUA2)
```

## UMGC1 Correlations among Writing Subscales (Criteria) Scores
```{r}
writeUMGC1<-global_ua2umgc1[global_ua2umgc1$college=="UMGC1",27:36]
rho <- lowerCor(writeUMGC1)
corPlot(rho, main = "Correlations among Writing Subscales, UMGC1")
```

## Correlations among Writing Subscales in the Combined Sample (UA2 and UMGC1)
```{r}
write<-global_ua2umgc1[,27:36]
rho <- lowerCor(write)
corPlot(rho, main = "Correlations among Writing Subscales, UA2 and UMGC1")
```

# Bar Graphs for Writing Subscales (Criteria) Scores
## UA2 Writing Subscales (Criteria) Scores
```{r}
barplot(table(global_ua2umgc1[global_ua2umgc1$college=="UA2",27]),
        main="Write_Summary Score Distribution, UA2",
        xlab="Write_Summary Score", ylab="Number of Students", border="purple", 
        col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1[global_ua2umgc1$college=="UA2",28]),
        main="Write_Suggestions Score Distribution, UA2",
        xlab="Write_Suggestion Score", ylab="Number of Students", 
        border="purple", col="grey", density=100)
```


```{r}
barplot(table(global_ua2umgc1[global_ua2umgc1$college=="UA2",29]),
        main="Write_Structure Score Distribution, UA2",
        xlab="Write_Structure Score", ylab="Number of Students", 
        border="purple", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1[global_ua2umgc1$college=="UA2",30]),
        main="Write_Transitions Score Distribution, UA2",
        xlab="Write_Transitions", ylab="Number of Students", 
        border="purple", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1[global_ua2umgc1$college=="UA2",31]),
        main="Write_Main_Idea Score Distribution, UA2",
        xlab="Write_Main_Idea", ylab="Number of Students", 
        border="purple", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1[global_ua2umgc1$college=="UA2",32]),
        main="Write_Cohesion Score Distribution, UA2",
        xlab="Write_Cohesion", ylab="Number of Students", 
        border="purple", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1[global_ua2umgc1$college=="UA2",33]),
        main="Write_Correct Score Distribution, UA2",
        xlab="Write_Correct", ylab="Number of Students", 
        border="purple", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1[global_ua2umgc1$college=="UA2",34]),
        main="Write_Complexity Score Distribution, UA2",
        xlab="Write_Complexity", ylab="Number of Students", 
        border="purple", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1[global_ua2umgc1$college=="UA2",35]),
        main="Write_Usage Score Distribution, UA2",
        xlab="Write_Usage", ylab="Number of Students", 
        border="purple", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1[global_ua2umgc1$college=="UA2",36]),
        main="Write_Punctuation Score Distribution, UA2",
        xlab="Write_Punctuation", ylab="Number of Students", 
        border="purple", col="grey", density=100)
```

## UMGC1 Writing Subscales (Criteria) Scores
```{r}
barplot(table(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",27]),
        main="Write_Summary Score Distribution, UMGC1",
        xlab="Write_Summary Score", ylab="Number of Students", border="red", 
        col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",28]),
        main="Write_Suggestions Score Distribution, UMGC1",
        xlab="Write_Suggestion Score", ylab="Number of Students", 
        border="red", col="grey", density=100)
```


```{r}
barplot(table(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",29]),
        main="Write_Structure Score Distribution, UMGC1",
        xlab="Write_Structure Score", ylab="Number of Students", 
        border="red", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",30]),
        main="Write_Transitions Score Distribution, UMGC1",
        xlab="Write_Transitions", ylab="Number of Students", 
        border="red", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",31]),
        main="Write_Main_Idea Score Distribution, UMGC1",
        xlab="Write_Main_Idea", ylab="Number of Students", 
        border="red", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",32]),
        main="Write_Cohesion Score Distribution, UMGC1",
        xlab="Write_Cohesion", ylab="Number of Students", 
        border="red", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",33]),
        main="Write_Correct Score Distribution, UMGC1",
        xlab="Write_Correct", ylab="Number of Students", 
        border="red", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",34]),
        main="Write_Complexity Score Distribution, UMGC1",
        xlab="Write_Complexity", ylab="Number of Students", 
        border="red", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",35]),
        main="Write_Usage Score Distribution, UMGC1",
        xlab="Write_Usage", ylab="Number of Students", 
        border="red", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",36]),
        main="Write_Punctuation Score Distribution, UMGC1",
        xlab="Write_Punctuation", ylab="Number of Students", 
        border="red", col="grey", density=100)
```

## Writing Subscales (Criteria) Scores for the Combined Sample (UA2 and UMGC1)
```{r}
barplot(table(global_ua2umgc1$write_summary),
        main="Write_Summary Score Distribution, UA2 and UMGC1",
        xlab="Write_Summary Score", ylab="Number of Students", border="black", 
        col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1$write_suggestions),
        main="Write_Suggestions Score Distribution, UA2 and UMGC1",
        xlab="Write_Suggestion Score", ylab="Number of Students", 
        border="black", col="grey", density=100)
```


```{r}
barplot(table(global_ua2umgc1$write_structure),
        main="Write_Structure Score Distribution, UA2 and UMGC1",
        xlab="Write_Structure Score", ylab="Number of Students", 
        border="black", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1$write_transitions),
        main="Write_Transitions Score Distribution, UA2 and UMGC1",
        xlab="Write_Transitions", ylab="Number of Students", 
        border="black", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1$write_ideas),
        main="Write_Main_Idea Score Distribution, UA2 and UMGC1",
        xlab="Write_Main_Idea", ylab="Number of Students", 
        border="black", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1$write_cohesion),
        main="Write_Cohesion Score Distribution, UA2 and UMGC1",
        xlab="Write_Cohesion", ylab="Number of Students", 
        border="black", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1$write_correct),
        main="Write_Correct Score Distribution, UA2 and UMGC1",
        xlab="Write_Correct", ylab="Number of Students", 
        border="black", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1$write_complexity),
        main="Write_Complexity Score Distribution, UA2 and UMGC1",
        xlab="Write_Complexity", ylab="Number of Students", 
        border="black", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1$write_usage),
        main="Write_Usage Score Distribution, UA2 and UMGC1",
        xlab="Write_Usage", ylab="Number of Students", 
        border="black", col="grey", density=100)
```

```{r}
barplot(table(global_ua2umgc1$write_punctuation),
        main="Write_Punctuation Score Distribution, UA2 and UMGC1",
        xlab="Write_Punctuation", ylab="Number of Students", 
        border="black", col="grey", density=100)
```