---
title: "DAACS_UA2_UMGC1_Writing Assessment_Parallel Analysis, EFA, and CFA"
author: "Oxana Rosca"
date: "2023-01-06"
output:
  pdf_document: default
  html_document: default
  word_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

DAACS Writing is a constructed-response assessment. It is a 10-item scale, where
each item is a score on one writing criteria. The scores were produced via LightSide (trained models), an open source, automated essay scoring program.

# Assessment of factor structure
Furr (2014):
A scale's dimensionality, or factor structure, refers to the number 
and nature of the variables reflected in its items. 
a) Dimensionality should be evaluated and considered in scale construction, use, 
and evaluation
b) Coefficient alpha is not an index of unidimensionality, the “eigenvalue 
greater than one” rule should be avoided, and oblique rotations are preferable 
to orthogonal rotations.
Each dimension should be scored separately, with each requiring psychometric 
evaluation. That is, each score obtained from a scale should reflect a single 
coherent psychological variable. If a score reflects a blend of non-correlated 
dimensions, then its psychological meaning is highly ambiguous. Thus, a 
unidimensional scale produces a single score representing the lone dimension 
reflected in its items.
If dimensions are correlated robustly (reflecting some shared deeper 
psychological variable), then scores from those dimensions might be combined to 
form a score reflecting their shared psychological variable.

## Results

The parallel analyses confirms the unidimensionality of the writing scale with 
the scores of ten writing criteria as indicators (the first eigenvalue 
substantially dominates other eigenvalues). The results of parallel analysis 
suggest 4 factors in the writing scale.However, the rubric for writing 
assessment suggests a five-factor structure by assigning 10 criteria to 5 groups: 
  Content includes Summary and Suggestions
  Organization	includes Structure and	Transitions
  Paragraphs includes	Focus on a Main Idea and	Cohesion
  Sentences	includes Correct and	Complex
  Conventions	includes Usage and	Punctuation
According to the results of EFA, for both colleges, the 5-factor model has a 
potential. However, the variables of Correct and Usage have to be adjusted: they 
are too easy for the UAlbany students.
The five-factor CFA model is misspecified to date.

```{r}
library(psych)
library(psychTools)
library(lavaan)
library(semPlot)
library(dplyr)
```
Test for the unidimensionality and number of factors in your data using parallel 
analysis and Exploratory FA
Load the data file
```{r}
global_ua2umgc1 <- 
  readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/global_ua2umgc1.rds")
```

## Parallel Analysis

### Unidimensionality rules of thumb (Dr. Colvin)
20% of var explained or 5:1 ratio for eigen 1 to eigen 2 are based on a PCA, 
where at least one of the eigenvalues must be >=1). Because FA, not PCA, takes 
into account measurement error, it's possible that you can have values less 
than 1, but it's not a good sign if your first one is so small.
Different scientists advocate for different ratios, some say 4:1, others 8:1.

### Combined Sample Parallel Analysis (UA2 and UMGC1)
```{r}
fa.parallel(global_ua2umgc1[,c(27:36)],fa="fa",fm="ml",n.iter=1000,
        main="Parallel Analysis Scree plot for Writing Scale, UA2 and UMGC1")
```

### UMGC1 Sample Parallel Analysis
```{r}
fa.parallel(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(27:36)],fm="ml",
          fa="fa",n.iter=1000,
          main="Parallel Analysis Scree plot for Writing Scale, UMGC1")
```

### UA2 Sample Parallel Analysis
```{r}
fa.parallel(global_ua2umgc1[global_ua2umgc1$college=="UA2",c(27:36)],fa="fa",
fm="ml",n.iter=1000,main="Parallel Analysis Scree plot for Writing Scale, UA2")
```
The parallel analysis on UA2 run with warnings "the standard deviation is zero."

####Standard Deviations of all writing criteria by college
```{r}
describe.by(global_ua2umgc1 [,27:36], global_ua2umgc1$college)
```
At UA2, the variables of write_correct and write_usage have very small sd, 0.09 
and 0.13 respectively.
At UMGC1, those variables have sd equal to 0.17 and 0.42 respectively.

#####Frequencies for write_correct and write_usage by college:
```{r}
table <- with(global_ua2umgc1,table(write_correct,college)) 
table
```

```{r}
table <- with(global_ua2umgc1,table(write_usage,college)) 
table
```

After removing the variables of write_correct and write_usage, the parallel 
analysis on UA2 data runs normally:
```{r}
fa.parallel(global_ua2umgc1[global_ua2umgc1$college == "UA2",c(27:32,34,36)],
            fa="fa",fm="ml",n.iter=1000,
               main="Parallel Analysis Scree plot for Writing Scale, UA2")
```

## Exploratory Factor Analysis (EFA)

### Combined (UA2 and UMGC1) Sample

#### 1-factor EFA, Combined Sample, all 10 criteria
```{r}
FA_write1 <- fa(global_ua2umgc1[,c(27:36)], nfactors=1, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(FA_write1, sort=TRUE)
```

##### 1-factor EFA, Combined Sample, without Correct and Usage
```{r}
FA_write1 <- fa(global_ua2umgc1[,c(27:32,34,36)], nfactors=1, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(FA_write1, sort=TRUE)
```

#### 2-factor EFA, Combined Sample, all 10 criteria
```{r}
FA_write2 <- fa(global_ua2umgc1[,c(27:36)], nfactors=2, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(FA_write2, sort=TRUE)
```
##### 2-factor EFA, Combined Sample, without Correct and Usage
```{r}
FA_write2 <- fa(global_ua2umgc1[,c(27:32,34,36)], nfactors=2, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(FA_write2, sort=TRUE)
```

#### 3-factor EFA, Combined Sample, all 10 criteria
Shows a good fit.
The variables of write_usage and write_transitions didn't load sufficiently 
(at least at 0.2 level) on any factor.
```{r}
FA_write3 <- fa(global_ua2umgc1[,c(27:36)], nfactors=3, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05,residuals=TRUE)
print(FA_write3, sort=TRUE, cut=0.2)
```
```{r}
fa.diagram(FA_write3, cut=0.2, 
           main= "3-factor EFA, all 10 criteria, UA2 and UMGC1")
```

##### Frequencies for the write_transitions scores by college:
```{r}
table <- with(global_ua2umgc1,table(write_transitions,college)) 
table
```
##### 3-factor EFA, 8 criteria, Combined Sample,  without Correct and Usage
Shows a good fit.
The variables of write_summary didn't load sufficiently on any factor.
```{r}
FA_write3 <- fa(global_ua2umgc1[,c(27:32,34,36)], nfactors=3, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05,residuals=TRUE)
print(FA_write3, sort=TRUE, cut=0.2)
```

```{r}
fa.diagram(FA_write3, cut=0.2, 
           main= "3-factor EFA, 8 criteria, UA2 and UMGC1")
```

```{r}
table <- with(global_ua2umgc1,table(write_summary,college)) 
table
```

#### 4-factor EFA, Combined Sample, all 10 criteria
Shows a good fit.
The variable of write_usage didn't load sufficiently on any factor.
```{r}
FA_write4 <- fa(global_ua2umgc1[,c(27:36)], nfactors=4, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(FA_write4, sort=TRUE, cut=0.2)
```

```{r}
fa.diagram(FA_write4, cut=0.2, 
           main= "4-factor EFA, 10 criteria, UA2 and UMGC1")
```

##### 4-factor EFA, Combined Sample, without Correct and Usage
```{r}
FA_write4 <- fa(global_ua2umgc1[,c(27:32,34,36)], nfactors=4, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(FA_write4, sort=TRUE)
```

#### 5-factor EFA, Combined Sample, all 10 criteria
Has a good fit.
The variables of write_complexity and write_correct didn't load sufficiently on 
any factor.
```{r}
FA_write5 <- fa(global_ua2umgc1[,c(27:36)], nfactors=5, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(FA_write5, sort=TRUE, cut=0.2)
```

```{r}
fa.diagram(FA_write5, cut=0.2, 
           main= "5-factor EFA, 10 criteria, UA2 and UMGC1")
```

##### 5-factor EFA, Combined Sample, without Correct and Usage

```{r}
FA_write5 <- fa(global_ua2umgc1[,c(27:32,34,36)], nfactors=5,rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(FA_write5, sort=TRUE)
```

#### 6-factor EFA, Combined Sample, all 10 criteria
```{r}
FA_write6 <- fa(global_ua2umgc1[,c(27:36)], nfactors=6, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(FA_write6, sort=TRUE)
```

##### 6-factor EFA, Combined Sample, without Correct and Usage
```{r}
FA_write6 <- fa(global_ua2umgc1[,c(27:32,34,36)], nfactors=6, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(FA_write6, sort=TRUE)
```

###UMGC1 Sample

#### 1-factor EFA, UMGC1, all 10 criteria
```{r}
FA_write1 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(27:36)], 
          nfactors=1,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write1, sort=TRUE)
```

##### 1-factor EFA, UMGC1, without Correct and Usage
```{r}
FA_write1 <-fa(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(27:32,34,36)], 
          nfactors=1,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write1, sort=TRUE)
```

#### 2-factor EFA, UMGC1, all 10 criteria
```{r}
FA_write2 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(27:36)], 
          nfactors=2,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write2, sort=TRUE)
```

##### 2-factor EFA, UMGC1, without Correct and Usage
```{r}
FA_write2 <-fa(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(27:32,34,36)], 
          nfactors=2,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write2, sort=TRUE)
```

#### 3-factor EFA, UMGC1, all 10 criteria
```{r}
FA_write3 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(27:36)], 
          nfactors=3,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write3, sort=TRUE)
```

##### 3-factor EFA, UMGC1, without Correct and Usage
```{r}
FA_write3 <-fa(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(27:32,34,36)], 
          nfactors=3,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write3, sort=TRUE)
```

#### 4-factor EFA, UMGC1, all 10 criteria
The model has a good fit.
The variable of write_usage didn't load sufficiently (at least at 0.3 level) on 
any factor.
```{r}
FA_write4 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(27:36)], 
          nfactors=4,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write4, sort=TRUE, cut=0.2)
```

```{r}
fa.diagram(FA_write4, cut=0.2, 
           main= "4-factor EFA, 10 criteria, UMGC1")
```

##### 4-factor EFA, UMGC1, without Correct and Usage
```{r}
FA_write4 <-fa(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(27:32,34,36)], 
          nfactors=4,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write4, sort=TRUE)
```

#### 5-factor EFA, UMGC1, all 10 criteria
```{r}
FA_write5 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(27:36)], 
          nfactors=5,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write5, sort=TRUE)
```

##### 5-factor EFA, UMGC1, without Correct and Usage
```{r}
FA_write5<-fa(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(27:32,34,36)], 
          nfactors=5,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write5, sort=TRUE)
```

#### 6-factor EFA, UMGC1, all 10 criteria
```{r}
FA_write6 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(27:36)], 
          nfactors=6,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write6, sort=TRUE)
```

##### 6-factor EFA, UMGC1, without Correct and Usage
```{r}
FA_write6 <-fa(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(27:32,34,36)], 
          nfactors=6,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write6, sort=TRUE)
```

### UA2 Sample

#### 1-factor EFA, UA2, all 10 criteria
```{r}
FA_write1 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UA2",c(27:36)], 
          nfactors=1,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write1, sort=TRUE)
```

##### 1-factor EFA, UA2, without Correct and Usage
```{r}
FA_write1 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UA2",c(27:32,34,36)], 
          nfactors=1,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write1, sort=TRUE)
```

#### 2-factor EFA, UA2, all 10 criteria
```{r}
FA_write2 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UA2",c(27:36)], 
          nfactors=2,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write2, sort=TRUE)
```

##### 2-factor EFA, UA2, without Correct and Usage
```{r}
FA_write2 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UA2",c(27:32,34,36)], 
          nfactors=2,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write2, sort=TRUE)
```

#### 3-factor EFA, UA2, all 10 criteria
```{r}
FA_write3 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UA2",c(27:36)], 
          nfactors=3,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write3, sort=TRUE)
```

##### 3-factor EFA, UA2, without Correct and Usage
The model has a good fit.
```{r}
FA_write3 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UA2",c(27:32,34,36)], 
          nfactors=3,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write3, sort=TRUE, cut=0.2)
```

```{r}
fa.diagram(FA_write3, cut=0.2, 
           main= "3-factor EFA, 8 criteria, UA2")
```

#### 4-factor EFA, UA2, all 10 criteria
The model has a good fit.
```{r}
FA_write4 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UA2",c(27:36)], 
          nfactors=4,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write4, sort=TRUE, cut=0.2)
```

```{r}
fa.diagram(FA_write4, cut=0.2, 
           main= "4-factor EFA, 10 criteria, UA2")
```

##### 4-factor EFA, UA2, without Correct and Usage
```{r}
FA_write4 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UA2",c(27:32,34,36)], 
          nfactors=4,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write4, sort=TRUE)
```

#### 5-factor EFA, UA2, all 10 criteria
The model has a good fit.
```{r}
FA_write5<- fa(global_ua2umgc1[global_ua2umgc1$college=="UA2",c(27:36)], 
          nfactors=5,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write5, sort=TRUE, cut=0.2)
```

```{r}
fa.diagram(FA_write5, cut=0.2, 
           main= "5-factor EFA, 10 criteria, UA2")
```

##### 5-factor EFA, UA2, without Correct and Usage
```{r}
FA_write5 <-fa(global_ua2umgc1[global_ua2umgc1$college=="UA2",c(27:32,34,36)], 
          nfactors=5,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write5, sort=TRUE)
```

```{r}
table <- with(global_ua2umgc1,table(write_punctuation,write_correct,college)) 
table
```

#### 6-factor EFA, UA2, all 10 criteria
```{r}
FA_write6 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UA2",c(27:36)], 
          nfactors=6,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write6, sort=TRUE)
```

##### 6-factor EFA, UA2, without Correct and Usage
```{r}
FA_write6 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UA2",c(27:32,34,36)], 
          nfactors=6,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write6, sort=TRUE)
```

## CFA
The CFAs confirm that the 5-factor model is misspecified. At least one of the 
correlations between factors is larger than 1, which is an impossible estimate. 
That, in turn, makes the modification indices invalid.

### Specify the 10-criteria-5-factor CFA model
```{r}
CFA_write5f<- 'content =~ write_summary + write_suggestions
organization =~ write_structure + write_transitions
paragraphs =~ write_ideas + write_cohesion
sentences =~ write_correct + write_complexity
conventions =~ write_usage + write_punctuation
content~~organization
content~~paragraphs
content~~sentences
content~~conventions
organization~~paragraphs
organization~~sentences
organization~~conventions
paragraphs~~sentences
paragraphs~~conventions
sentences~~conventions'
```

### Run the CFA model, Combined Sample (UA2 and UMGC1)
The covariance matrix of latent variables for the CFA model is not 
positive definite (lavaan WARNING).
```{r}
CFA_write5f_ua2umgc1_fit<-cfa(CFA_write5f,
                data=global_ua2umgc1[,c(27:36)],std.lv=TRUE, orthogonal=FALSE)
summary(CFA_write5f_ua2umgc1_fit, standardized=TRUE, fit.measures = TRUE)
```

```{r}
semPaths(CFA_write5f_ua2umgc1_fit,what="path",layout="tree2",whatLabels="path",
        rotation=2)
```


Investigate the model. There is a correlation greater than 1:
```{r}
lavInspect(CFA_write5f_ua2umgc1_fit, "cor.lv")
```

#### Request Modification Indecies for Combined Sample (UA2 and UMGC1) CFA.
lavaan WARNING: starting values imply a correlation larger than 1.
```{r}
modindices(CFA_write5f_ua2umgc1_fit, sort = TRUE, maximum.number = 5)
```

### Run the 10-criteria-5-factor model for UA2 sample
The covariance matrix of latent variables for the CFA model is not 
positive definite (lavaan WARNING).
```{r}
CFA_write5f_ua2_fit<-cfa(CFA_write5f,
                data=global_ua2umgc1[global_ua2umgc1$college=="UA2",c(27:36)],
                std.lv=TRUE, orthogonal=FALSE)
summary(CFA_write5f_ua2_fit, fit.measures = TRUE)
```

Investigate. There are 4 correlations greater than 1:
```{r}
lavInspect(CFA_write5f_ua2_fit, "cor.lv")
```

#### Request Modification Indecies for UA2 CFA
lavaan WARNING: starting values imply a correlation larger than 1
```{r}
modindices(CFA_write5f_ua2_fit, sort = TRUE, maximum.number = 5)
```

### Run the 10-criteria-5-factor model for UMGC1 sample
The covariance matrix of latent variables for the 10-criteria model is not 
positive definite (lavaan WARNING).
```{r}
CFA_write5f_umgc1_fit<-cfa(CFA_write5f,
                data=global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(27:36)],
                std.lv=TRUE, orthogonal=FALSE)
summary(CFA_write5f_umgc1_fit, fit.measures = TRUE)
```

Investigate. There are 3 correlations greater than 1:
```{r}
lavInspect(CFA_write5f_umgc1_fit, "cor.lv")
```

#### Request Modification Indecies for UMGC1 CFA
lavaan WARNING: starting values imply a correlation larger than 1
```{r}
modindices(CFA_write5f_umgc1_fit, sort = TRUE, maximum.number = 5)
```
 

After clarifying the scale's structure (CFA), examine the reliability and 
validity of each dimension through a series of studies (Furr, 2014).


#Reference
Furr, R. M. (2014). Scale construction and psychometrics for social and 
personality psychology.Thousand Oaks, CA: SAGE.doi:10.4135/9781446287866




