---
title: "DAACS_Combining Datasets from Different Colleges_2022_OR"
author: "Oxana Rosca"
date: "2022-11-14"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(haven)
library(dplyr)
```

#("D:OneDrive - University at Albany - SUNY/WorkDirectory")

Load data files
```{r}
umgc1SRLDaacs <- readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/ua2ReadDaacs.rds")
ua2ReadDaacs <- readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/ua2ReadDaacs.rds")
ua2MathDaacs <- readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/ua2MathDaacs.rds")
umgc1ReadDaacs <- readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/umgc1ReadDaacs.rds")
umgc1MathDaacs <- readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/umgc1MathDaacs.rds")
ua2SRLDaacs <- readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/ua2SRLDaacs.rds")
umgc1SRLDaacs <- readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/umgc1SRLDaacs.rds")
ua2ReadSpeedy <- readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/ua2ReadSpeedy.rds")
ua2MathSpeedy <- readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/ua2MathSpeedy.rds")
umgc1ReadSpeedy <- readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/umgc1ReadSpeedy.rds")
umgc1MathSpeedy <- readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/umgc1MathSpeedy.rds")
umgc1WriteSpeedy <- readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/umgc1WriteSpeedy.rds")
```

*Combine*
Combine the data sets:
```{r}
ua2umgc1ReadDaacs<-rbind(umgc1ReadDaacs, ua2ReadDaacs)
ua2umgc1ReadDaacs<-ua2umgc1ReadDaacs[,-c(25:35)]#to remove math total and domains
ua2umgc1MathDaacs<-rbind(umgc1MathDaacs, ua2MathDaacs)
ua2umgc1MathDaacs<-ua2umgc1MathDaacs[,-c(36:45)]#to remove reading total and domains
ua2umgc1SRLDaacs<-rbind(umgc1SRLDaacs, ua2SRLDaacs)
ua2umgc1SRLDaacs<-ua2umgc1SRLDaacs[,-c(25:45)]#to remove reading and math totals and domains
ua2umgc1MathReadDaacs<-merge(ua2umgc1MathDaacs,ua2umgc1ReadDaacs,all = TRUE)
ua2umgc1MathReadDaacs_Check<-
 ua2umgc1MathReadDaacs[rowSums(is.na(ua2umgc1MathReadDaacs))!=ncol(ua2umgc1MathReadDaacs),]
global_ua2umgc1<- merge(ua2umgc1MathReadDaacs,ua2umgc1SRLDaacs,all = TRUE)
global_ua2umgc1_Check<-
  global_ua2umgc1[rowSums(is.na(global_ua2umgc1))!=ncol(global_ua2umgc1),]
table(duplicated(global_ua2umgc1$DAACS_ID))
```
Comparing the # of cases in the _Check dataframes, there are no empty rows in 
new datasets. There are no duplicate DAACS_IDs either.

*College*
```{r}
ua2umgc1MathReadDaacs$college<-as.factor(ua2umgc1MathReadDaacs$college)
ua2umgc1ReadDaacs$college<-as.factor(ua2umgc1ReadDaacs$college)
ua2umgc1MathDaacs$college<-as.factor(ua2umgc1MathDaacs$college)
ua2umgc1SRLDaacs$college<-as.factor(ua2umgc1SRLDaacs$college)
global_ua2umgc1$college<-as.factor(global_ua2umgc1$college)
```

*Save New Files*
```{r}
saveRDS(ua2umgc1MathReadDaacs, file = 'ua2umgc1MathReadDaacs.rds')#library(haven)
write_sav(ua2umgc1MathReadDaacs, "ua2umgc1MathReadDaacs.sav")
write.table(ua2umgc1MathReadDaacs, 'ua2umgc1MathReadDaacs.csv', sep=',')
saveRDS(ua2umgc1ReadDaacs, file = 'ua2umgc1ReadDaacs.rds')
write_sav(ua2umgc1ReadDaacs, "ua2umgc1ReadDaacs.sav")
write.table(ua2umgc1ReadDaacs, 'ua2umgc1ReadDaacs.csv', sep=',')
saveRDS(ua2umgc1MathDaacs, file = 'ua2umgc1MathDaacs.rds')
write_sav(ua2umgc1MathDaacs, "ua2umgc1MathDaacs.sav")
write.table(ua2umgc1MathDaacs, 'ua2umgc1MathDaacss.csv', sep=',')
saveRDS(ua2umgc1SRLDaacs, file = 'ua2umgc1SRLDaacs.rds')
write.table(ua2umgc1SRLDaacs, 'ua2umgc1SRLDaacs.csv', sep=',')
saveRDS(global_ua2umgc1, file = 'global_ua2umgc1.rds')
write_sav(global_ua2umgc1, "global_ua2umgc1.sav")
write.table(global_ua2umgc1, 'global_ua2umgc1.csv', sep=',')
```

*Speedy Students*
prepare the speedy datafiles:
```{r}
ua2ReadSpeedy<-ua2ReadSpeedy[,-c(25:35)]#to remove math total and domains
umgc1ReadSpeedy<-umgc1ReadSpeedy[,-c(25:35)]
ua2MathSpeedy<-ua2MathSpeedy[,-c(36:45)]#to remove reading total and domains
umgc1MathSpeedy<-umgc1MathSpeedy[,-c(36:45)]
```

To combine all speedy students, who took less than 3.5 minutes for the reading 
assessment and/or less than 3 minutes for the math assessment, into a single 
data frame:
1)
```{r}
SPEEDYua2MathReadDaacs<-
 merge(ua2ReadSpeedy,ua2MathSpeedy,by.x =c(1:24,35:50),
       by.y = c(1:24,36:51),all.y = TRUE, all.x = TRUE)
SPEEDYumgc1MathReadDaacs<-
 merge(umgc1ReadSpeedy,umgc1MathSpeedy,
       by.x =c(1:24,35:50),by.y = c(1:24,36:51),all.y = TRUE, all.x = TRUE)
```

2) Adding new variables of college and item mQ157:
```{r}
SPEEDYua2MathReadDaacs$college <- 'UA2'
SPEEDYua2MathReadDaacs$mQ157 <- 'NA'
SPEEDYumgc1MathReadDaacs$college <- 'UMGC1'
```
3)
```{r}
SPEEDYua2umgc1MathReadDaacs<-
  rbind(SPEEDYua2MathReadDaacs,SPEEDYumgc1MathReadDaacs)
```

*Save New Files*
```{r}
saveRDS(SPEEDYua2umgc1MathReadDaacs, file = 'SPEEDYua2umgc1MathReadDaacs.rds')
write_sav(SPEEDYua2umgc1MathReadDaacs, "SPEEDYua2umgc1MathReadDaacs.sav")
write.table(SPEEDYua2umgc1MathReadDaacs,'SPEEDYua2umgc1MathReadDaacs.csv',sep=',')
```

