---
title: "DAACS_UA2_UMGC1_Correlations_OR"
author: "Oxana Rosca"
date: "2022-11-16"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(psych)
library(haven)
```

Load the data file
```{r}
global_ua2umgc1 <- readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/global_ua2umgc1.rds")
```

Total Number of Participants and Demographics or how many participants and 
variables you have:
```{r}
dim(global_ua2umgc1)
```

*Duplicates*
Test for duplicate values in read.items.response
Frequencies: How many of non-duplicated IDs?
```{r}
table(duplicated(global_ua2umgc1$DAACS_ID))
```
To check if there are empty rows:
```{r}
global_ua2umgc1_Check<-
  global_ua2umgc1[rowSums(is.na(global_ua2umgc1))!=ncol(global_ua2umgc1),]
```
Comparing the # of cases in umgc1SRLDaacs and umgc1SRLDaacs_Check (which are 
equal), there are no empty rows in umgc1SRLDaacs.


see the minimum value in minutes
```{r}
min(global_ua2umgc1$readTime, na.rm = TRUE)
min(global_ua2umgc1$mathTime, na.rm = TRUE)
```

*Correlations Total (UA2 and UMGC1 as one  sample)*

Introducing levels to the variable of college, we assign 1 and purple color to 
UA2 and 2 and red color to UMGC1.
Thus, a positive correlation of a variable with "college" means that UMGC1 
students are doing better; a negative correlation of a variable with "college" 
means that UA2 students are doing better.

For fewer than 11 variables, do a SPLOM (Scatter Plot Matrix) of the data.

Total Scores
```{r}
pairs.panels(global_ua2umgc1[,c (41,21,49,236,39)],bg=c("purple",
      "red")[global_ua2umgc1$college], stars=TRUE, pch=21,
          main="Correlations between Total Scores")
```

SRL Scales
```{r}
pairs.panels(global_ua2umgc1[,c (41,3:6,21,49,236,39)], stars=TRUE,
             bg=c("purple","red")[global_ua2umgc1$college], pch=21, gap=0,
                  main="Correlations between SRL Scales and Total Scores")
```

SRL Strategies Subscales
```{r}
pairs.panels(global_ua2umgc1[,c (41,3,7:10,21,49,236,39)],stars=TRUE,
             bg=c("purple","red")[global_ua2umgc1$college], pch=21, gap=0,
                main="Correlations between Strategies Scales and Total Scores")
```

SRL Motivation Subscales
```{r}
pairs.panels(global_ua2umgc1[,c (41,4, 11:13,21,49,236,39)],stars=TRUE,
             bg=c("purple","red")[global_ua2umgc1$college], pch=21, gap=0,
                main="Correlations between Motivation Scales and Total Scores")
```
SRL Metacognition Subscales
```{r}
pairs.panels(global_ua2umgc1[,c (41,5,14:16,21,49,236,39)],stars=TRUE,
            bg=c("purple","red")[global_ua2umgc1$college], pch=21, gap=0,
              main="Correlations between Metacognition Scales and Total Scores")
```

SRL Self-Efficacy Scales
```{r}
pairs.panels(global_ua2umgc1[,c (41,6, 17:20,21,49,236,39)], stars=TRUE,
            bg=c("purple","red")[global_ua2umgc1$college], pch=21, gap=0,
              main="Correlations between Self-Efficacy Scales and Total Scores")
```

Math Domains Subscales
```{r}
pairs.panels(global_ua2umgc1[,c (41,17,43:49)],stars=TRUE,
            bg=c("purple","red")[global_ua2umgc1$college], pch=21, gap=0,
              main="Correlations between Math Domains")
```
Reading Domains Subscales
```{r}
pairs.panels(global_ua2umgc1[,c (41,19,231:236)],stars=TRUE,
             bg=c("purple","red")[global_ua2umgc1$college], pch=21, gap=0,
              main="Correlations between Reading Domains")
```
Writing Criteria Subscales
```{r}
pairs.panels(global_ua2umgc1[,c (41,20,27:36,39)],stars=TRUE,
            bg=c("purple","red")[global_ua2umgc1$college], pch=21, gap=0,
              main="Correlations between Writing Domains")
```

*Correlations for UA2*
Subset UA2 data
```{r}
global_ua2 <- global_ua2umgc1[ which(global_ua2umgc1$college=='UA2'), ]
```

Total Scores
```{r}
pairs.panels(global_ua2[,c (21,49,236,39)],stars=TRUE, hist.col='purple4',
          main="Correlations between UA2 Total Scores")
```

SRL Scales
```{r}
pairs.panels(global_ua2[,c (3:6,21,49,236,39)], stars=TRUE,gap=0,
 hist.col='purple4',main="Correlations between UA2 SRL Scales and Total Scores")
```

SRL Strategies Subscales
```{r}
pairs.panels(global_ua2[,c (3,7:10,21,49,236,39)],stars=TRUE, gap=0,
hist.col='purple4',main="Correlations between UA2 SRL Strategies Scales and Total Scores")
```

SRL Motivation Subscales
```{r}
pairs.panels(global_ua2[,c (4,11:13,21,49,236,39)],stars=TRUE, gap=0,
 hist.col='purple4',main="Correlations between UA2 SRL Motivation Scales and Total Scores")
```
SRL Metacognition Subscales
```{r}
pairs.panels(global_ua2[,c (5,14:16,21,49,236,39)],stars=TRUE, gap=0,
 hist.col='purple4',main="Correlations between UA2 SRL Metacognition Scales and Total Scores")
```

SRL Self-Efficacy Scales
```{r}
pairs.panels(global_ua2[,c (6,17:20,21,49,236,39)], stars=TRUE, gap=0,
 hist.col='purple4',main="Correlations between UA2 SRL Self-Efficacy Scales and Total Scores")
```

Math Domains Subscales
```{r}
pairs.panels(global_ua2[,c (17,43:49)],stars=TRUE, gap=0,
 hist.col='purple4',main="Correlations between UA2 Math Domains")
```
Reading Domains Subscales
```{r}
pairs.panels(global_ua2[,c (19,231:236)],stars=TRUE, gap=0,
hist.col='purple4',main="Correlations between UA2 Reading Domains" )
```
Writing Criteria Subscales
```{r}
pairs.panels(global_ua2[,c (20,27:36,39)],stars=TRUE,gap=0, 
             hist.col='purple4',main="Correlations between UA2 Writing Domains")
```


*Correlations for UMGC1*
Subset UMGC1 data
```{r}
global_umgc1 <- global_ua2umgc1[ which(global_ua2umgc1$college=='UMGC1'), ]
```

Total Scores
```{r}
pairs.panels(global_umgc1[,c (21,49,236,39)],stars=TRUE, hist.col='red3',
          main="Correlations between UMGC1 Total Scores")
```

SRL Scales
```{r}
pairs.panels(global_umgc1[,c (3:6,21,49,236,39)], stars=TRUE,gap=0,
 hist.col='red3',main="Correlations between UMGC1 SRL Scales and Total Scores")
```

SRL Strategies Subscales
```{r}
pairs.panels(global_umgc1[,c (3,7:10,21,49,236,39)],stars=TRUE, gap=0,
hist.col='red3',main="Correlations between UMGC1 SRL Strategies Scales and Total Scores")
```

SRL Motivation Subscales
```{r}
pairs.panels(global_umgc1[,c (4,11:13,21,49,236,39)],stars=TRUE, gap=0,
 hist.col='red3',main="Correlations between UMGC1 SRL Motivation Scales and Total Scores")
```
SRL Metacognition Subscales
```{r}
pairs.panels(global_umgc1[,c (5,14:16,21,49,236,39)],stars=TRUE, gap=0,
 hist.col='red3',main="Correlations between UMGC1 SRL Metacognition Scales and Total Scores")
```

SRL Self-Efficacy Scales
```{r}
pairs.panels(global_umgc1[,c (6,17:20,21,49,236,39)], stars=TRUE, gap=0,
 hist.col='red3',main="Correlations between UMGC1 SRL Self-Efficacy Scales and Total Scores")
```

Math Domains Subscales
```{r}
pairs.panels(global_umgc1[,c (17,43:49)],stars=TRUE, gap=0,
 hist.col='red3',main="Correlations between UMGC1 Math Domains")
```
Reading Domains Subscales
```{r}
pairs.panels(global_umgc1[,c (19,231:236)],stars=TRUE, gap=0,
hist.col='red3',main="Correlations between UMGC1 Reading Domains" )
```
Writing Criteria Subscales
```{r}
pairs.panels(global_umgc1[,c (20,27:36,39)],stars=TRUE,gap=0,
 hist.col='red3', main="Correlations between UMGC1 Writing Domains")
```

*Check new files*
Test for duplicate values in read.items.response
Frequencies: How many of non-duplicated IDs?
```{r}
table(duplicated(global_ua2$DAACS_ID))
table(duplicated(global_umgc1$DAACS_ID))
```
To check if there are empty rows:
```{r}
global_ua2_Check<-
  global_ua2[rowSums(is.na(global_ua2))!=ncol(global_ua2),]
global_umgc1_Check<-
  global_umgc1[rowSums(is.na(global_umgc1))!=ncol(global_umgc1),]
```
Comparing the # of cases in global_ua2 and global_ua2_Check (which are equal), 
there are no empty rows in global_ua2. Comparing the # of cases in global_umgc1 
and global_umgc1_Check (which are equal), there are no empty rows in 
global_umgc1.

*Save New File*

```{r}
saveRDS(global_ua2, file = 'global_ua2.rds')
write_sav(global_ua2, "global_ua2.sav")#library(haven)
write.table(global_ua2, 'global_ua2.csv', sep=',')
saveRDS(global_umgc1, file = 'global_umgc1.rds')
write_sav(global_umgc1, "global_umgc1.sav")#library(haven)
write.table(global_umgc1, 'global_umgc1.csv', sep=',')
```