---
title: "DAACS_math_DataOrganizing_UMGC1_Sep16_2022_OR"
author: "Oxana Rosca"
date: "2022-11-13"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(psych)
library(ggplot2)
library(maditr)
library(stringr)
library(haven)
```

If needed:
setwd("D:OneDrive - University at Albany - SUNY/WorkDirectory")

Load data files
```{r}
load("data_export/DAACS-Results-umgc_2022-09-16.rda")
```

```{r}
umgc1.math.items.questions<-math.items.questions
```

Use str_replace() method from stringr package to replace part of a column string 
with another string in R DataFrame.
```{r}
math.items$qid <- str_replace(math.items$qid,"Q", "mQ")
```

*Duplicates*
Test for duplicate values in math.items.response
Frequencies: How many of non-duplicated IDs?
```{r}
table(duplicated(daacs$DAACS_ID))
```

```{r}
table(duplicated(math.items$DAACS_ID))
```
math.items is a long dataset with many rows per a test-taker

*Attempts*
How many of each number of attempts?
```{r}
table(math.items$attempt, useNA = 'ifany') %>% print() %>% prop.table()* 100
```
Select the first attempts only
```{r}
math.items <- math.items [math.items$attempt == "1",]
```

*Restructure*
re-structure =long dataset from wide dataset
```{r}
umgc1MathDaacs <- dcast(math.items,DAACS_ID ~ qid,value.var = 'score')
```

*Merge*
Using all.y = TRUE so that we use only students provided from 
umgc1. These are all newly enrolled students' data on Sep 16th, 2022 (Removing 
all students that did not take math assessment)
```{r}
umgc1MathDaacs <- merge(daacs,umgc1MathDaacs,by = 'DAACS_ID', all.y = TRUE)
```

*Test Time*
Calculate test time in minutes per student:
```{r}
umgc1MathDaacs$mathTime= (umgc1MathDaacs$mathCompletionDate - 
                            umgc1MathDaacs$mathStartDate)/60
```

To remove the non-numeric substring "sec" from the values of mathTime
```{r}
time_var_temp <- 
lapply(umgc1MathDaacs[237],function(x)as.numeric(sub("\\s+\\D+$","",x)))
time_var_temp<-as.data.frame(time_var_temp)
View(time_var_temp)
umgc1MathDaacs$mathTime<-time_var_temp$mathTime
View(umgc1MathDaacs)
```


see the minimum value in minutes
```{r}
min(umgc1MathDaacs$mathTime)
```

What is the shortest time for a student to get a perfect score
```{r}
min(umgc1MathDaacs[umgc1MathDaacs$mathTotal == 1.0,]$mathTime)
```
To get at least 70%
```{r}
min(umgc1MathDaacs[umgc1MathDaacs$mathTotal >= .7,]$mathTime)
```
How many took less than 3 minutes
```{r}
nrow(umgc1MathDaacs[umgc1MathDaacs$mathTime <= 3,])
```
To create a separate dataset of speedy students,
1)Create a vector of the row numbers of the speedy students:
```{r}
speedy<-which (umgc1MathDaacs$mathTime <= 3)
```

2)subset the rows of the speedy students as a dataframe:
```{r}
umgc1MathSpeedy<-umgc1MathDaacs[speedy, ]
umgc1MathSpeedy[,c(1,32,237)]
```

```{r}
umgc1MathSpeedy$DAACS_ID
```
11 speedy students with DAACS_ID 34, 174, 204, 396  428, 522, 745, 807,  984, 
1011, and 1032 took less than 3.5 minutes for the reading assessment and less 
than 3 minutes for the math assessment.
23 speedy students with DAACS_ID 1, 49, 132, 219,  261,  298,  327,  373,  421,  
464,  465,  559,  602,  617,  695, 823,  878,  885,  961,  971,  980,  990, and 
992 took less than 3 minutes for the math assessment.

Remove 34 speedy students (who completed the assesments in 3 minutes or less)
```{r}
umgc1MathDaacs <- umgc1MathDaacs[umgc1MathDaacs$mathTime > 3,]
```

*Total Score*
Histogram of the math scores in points
```{r}
ggplot(umgc1MathDaacs, aes(x = mathTotal)) + 
  geom_histogram(binwidth = 0.055, show.legend = TRUE, color = "red", 
                 fill = "#999999", alpha = 1) + xlab('math Total') +   
                    ylab('Number of Students')
```
Cut the variable of scores into three categories of dots
```{r}
umgc1MathDaacs$mathTotalDots <- cut(umgc1MathDaacs$mathTotal,
                        breaks=c(0, 0.65, 0.85, 1),labels=c('1', '2', '3'))
```

To build a bar-plot of the math scores in dots
```{r}
table(umgc1MathDaacs$mathTotalDots)
```

```{r}
barplot(table(umgc1MathDaacs$mathTotalDots),
        main="UMGC1 math Total Score in Dots",
          xlab="math Total in Dots", ylab="Number of Students", border="red", 
              col="grey", density=100)
```


To check if there are empty rows:
```{r}
umgc1MathDaacs_Check<-
  umgc1MathDaacs[rowSums(is.na(umgc1MathDaacs))!=ncol(umgc1MathDaacs),]
```
Comparing the # of cases, there are no empty rows

*Save New File*
Adding a variable of college and saving the new data file:
```{r}
umgc1MathDaacs$college <- 'UMGC1'
saveRDS(umgc1MathDaacs, file = 'umgc1MathDaacs.rds')
write_sav(umgc1MathDaacs, "umgc1MathDaacs.sav")
write.table(umgc1MathDaacs, 'umgc1MathDaacs.csv', sep=',')
saveRDS(umgc1MathSpeedy, file = 'umgc1MathSpeedy.rds')
write_sav(umgc1MathSpeedy, "umgc1MathSpeedy.sav")
write.table(umgc1MathSpeedy, 'umgc1MathSpeedy.csv', sep=',')
```

*Total Number of Participants and Demographics*
how many paricipants and variables you have 
```{r}
dim(umgc1MathDaacs)
```