---
title: "DAACS_UA2_UMGC1_Writing Assessment_Parallel Analysis and EFA"
author: "Oxana Rosca"
date: "2023-01-06"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*Results*
The Writing scale consists of 10 criteria. 
The results of parallel analysis suggest 4 factors in the writing scale.However, 
the rubric for writing assessment suggests a five-factor structure by assigning 
10 criteria to 5 groups: 
  Content includes Summary and Suggestions
  Organization	includes Structure and	Transitions
  Paragraphs includes	Focus on a Main Idea and	Cohesion
  Sentences	includes Correct and	Complex
  Conventions	includes Usage and	Punctuation
According to the results of EFA, for the both colleges, the best fit produced 
the 5-factor models, where summary and suggestions load on a single factor, 
 UMGC1: TLI = 0.97, RMSEA[95% CI]= 0.031[0,0.063]	
  UA2: TLI = 0.987, RMSEA[95% CI]= 0.023[0,0.056]

```{r}
library(psych)
library(psychTools)
```

Load the data file
```{r}
global_ua2umgc1 <- readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/global_ua2umgc1.rds")
```
*Assessment of factor structure*
*Unidimensionality rules of thumb (Dr. Colvin)*:
20% of var explained or 5:1 ratio for eigen 1 to eigen 2 are based on a PCA, 
where at least one of the eigenvalues must be >=1). Because FA, not PCA, takes 
into account measurement error, it's possible that you can have values less 
than 1, but it's not a good sign that your first one is so small.
Different people advocate for different ratios, some say 4:1, others 8:1.

*Exploratory Factor Analysis (EFA)*
Furr, R. M. (2014). Scale construction and psychometrics for social and 
personality psychology.Thousand Oaks, CA: SAGE.doi:10.4135/9781446287866:
A scale's dimensionality, or factor structure, refers to the number and nature 
of the variables reflected in its items. 
a) Dimensionality should be evaluated and considered in scale construction, use, 
and evaluation
b) Coefficient alpha is not an index of unidimensionality, the “eigenvalue 
greater than one” rule should be avoided, and oblique rotations are preferable 
to orthogonal rotations.
Each dimension should be scored separately, with each requiring psychometric 
evaluation. That is, each score obtained from a scale should reflect a single 
coherent psychological variable. If a score reflects a blend of non-correlated 
dimensions, then its psychological meaning is highly ambiguous. Thus, a 
unidimensional scale produces a single score representing the lone dimension 
reflected in its items.
If dimensions are correlated robustly (reflecting some shared deeper 
psychological variable), then scores from those dimensions might be combined to 
form a score reflecting their shared psychological variable.
Test for the number of factors (Exploratory FA) in your data using parallel 
analysis

*Combined Sample (UA2 and UMGC1)*
*Parallel Analysis*
The parallel analyses confirms the unidimensionality of the writing scale with 
the scores of ten writing criteria as indicators (the first eigenvalue 
substantially dominates other eigenvalues)
```{r}
fa.parallel(global_ua2umgc1[,c(27:36)],fa="fa",fm="ml",n.iter=1000,
        main="Parallel Analysis Scree plot for Writing Scale, UA2 and UMGC1")
```
*Exploratory Factor Analysis*

1-factor
Write_correct and write_usage do not load sufficiently on a general factor
```{r}
FA_write1 <- fa(global_ua2umgc1[,c(27:36)], nfactors=1, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(FA_write1, sort=TRUE)
```

2-factor
```{r}
FA_write2 <- fa(global_ua2umgc1[,c(27:36)], nfactors=2, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(FA_write2, sort=TRUE)
```

3-factor
```{r}
FA_write3 <- fa(global_ua2umgc1[,c(27:36)], nfactors=3, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(FA_write3, sort=TRUE)
```

4-factor
```{r}
FA_write4 <- fa(global_ua2umgc1[,c(27:36)], nfactors=4, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(FA_write4, sort=TRUE)
```
5-factor
```{r}
FA_write5 <- fa(global_ua2umgc1[,c(27:36)], nfactors=5, rotate="oblimin", 
                SMC=TRUE, max.iter=1000, fm="ml", alpha=.05)
print(FA_write5, sort=TRUE)
```

*UMGC1 Sample*
*Parallel Analysis*

```{r}
fa.parallel(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(27:36)],fm="ml",
          fa="fa",n.iter=1000,
          main="Parallel Analysis Scree plot for Writing Scale, UMGC1")

```
*Exploratory Factor Analysis*
1-factor
```{r}
FA_write1 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(27:36)], 
          nfactors=1,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write1, sort=TRUE)
```

2-factor
```{r}
FA_write2 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(27:36)], 
          nfactors=2,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write2, sort=TRUE)
```

3-factor
```{r}
FA_write3 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(27:36)], 
          nfactors=3,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write3, sort=TRUE)
```

4-factor
```{r}
FA_write4 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(27:36)], 
          nfactors=4,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write4, sort=TRUE)
```
5-factor
```{r}
FA_write5 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UMGC1",c(27:36)], 
          nfactors=5,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write5, sort=TRUE)
```

*UA2 Sample*
*Parallel Analysis*

```{r}
fa.parallel(global_ua2umgc1[global_ua2umgc1$college == "UA2",c(27:36)],fa="fa",
        fm="ml",n.iter=1000,
        main="Parallel Analysis Scree plot for Writing Scale, UA2")
```

*Exploratory Factor Analysis*
1-factor
```{r}
FA_write1 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UA2",c(27:36)], 
          nfactors=1,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write1, sort=TRUE)
```

2-factor
```{r}
FA_write2 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UA2",c(27:36)], 
          nfactors=2,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write2, sort=TRUE)
```

3-factor
```{r}
FA_write3 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UA2",c(27:36)], 
          nfactors=3,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write3, sort=TRUE)
```

4-factor
```{r}
FA_write4 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UA2",c(27:36)], 
          nfactors=4,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write4, sort=TRUE)
```
5-factor
```{r}
FA_write5 <- fa(global_ua2umgc1[global_ua2umgc1$college=="UA2",c(27:36)], 
          nfactors=5,rotate="oblimin",SMC=TRUE,max.iter=1000,fm="ml",alpha=.05)
print(FA_write5, sort=TRUE)
```

After clarifying the scale's structure (CFA), examine the reliability and 
validity of each dimension through a series of studies (Furr, 2014).







