---
title: "Numbers of Test-Takers for All Assessments"
author: "Oxana Rosca"
date: "2022-12-22"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyr)
```


Load the data file
```{r}
global_ua2umgc1 <- 
  readRDS("D:/OneDrive - University at Albany - SUNY/WorkDirectory/data_export/global_ua2umgc1.rds")
```

How many students took all four assessments?
```{r}
allFour<- global_ua2umgc1%>% tidyr::drop_na(21,49,236,39)
nrow (allFour)
```
How many students per college took all four assessments?
```{r}
table(allFour$college)
```
How many students took SRL assessment?
```{r}
SRL<- global_ua2umgc1%>% tidyr::drop_na(21)
nrow (SRL)
```
How many students per college took SRL assessment?
```{r}
table(SRL$college)
```
How many students took Math assessment?
```{r}
Math<- global_ua2umgc1%>% tidyr::drop_na(49)
nrow (Math)
```
How many students per college took Math assessment?
```{r}
table(Math$college)
```
How many students took Reading assessment?
```{r}
Read<- global_ua2umgc1%>% tidyr::drop_na(236)
nrow (Read)
```
How many students per college took Reading assessment?
```{r}
table(Read$college)
```
How many students took Writing assessment?
```{r}
Write<- global_ua2umgc1%>% tidyr::drop_na(39)
nrow (Write)
```
How many students per college took Writing assessment?
```{r}
table(Write$college)
```

How many students took SRL, Math, and Reading assessments?
```{r}
noWrite<- global_ua2umgc1%>% tidyr::drop_na(21,49,236)
nrow (noWrite)
```
How many students per college took SRL, Math, and Reading assessments?
```{r}
table(noWrite$college)
```

How many students took SRL, Math, and Writing assessments?
```{r}
noRead<- global_ua2umgc1%>% tidyr::drop_na(21,49,39)
nrow (noRead)
```
How many students per college took SRL, Math, and Writing assessments?
```{r}
table(noRead$college)
```

How many students took SRL, Reading, and Writing assessments?
```{r}
noMath<- global_ua2umgc1%>% tidyr::drop_na(21,236,39)
nrow (noMath)
```
How many students per college took SRL, Reading, and Writing assessments?
```{r}
table(noMath$college)
```

How many students took Math, Reading, and Writing assessments?
```{r}
noSRL<- global_ua2umgc1%>% tidyr::drop_na(49,236,39)
nrow (noSRL)
```
How many students per college took Math, Reading, and Writing assessments?
```{r}
table(noSRL$college)
```

How many students took SRL and Math assessments?
```{r}
srlMath<- global_ua2umgc1%>% tidyr::drop_na(21,49)
nrow (srlMath)
```
How many students per college took SRL and Math assessments?
```{r}
table(srlMath$college)
```

How many students took SRL and Reading assessments?
```{r}
srlRead<- global_ua2umgc1%>% tidyr::drop_na(21,236)
nrow (srlRead)
```
How many students per college took SRL and Reading assessments?
```{r}
table(srlRead$college)
```

How many students took SRL and Writing assessments?
```{r}
srlWrite<- global_ua2umgc1%>% tidyr::drop_na(21,39)
nrow (srlWrite)
```
How many students per college took SRL and Writing assessments?
```{r}
table(srlWrite$college)
```

How many students took Math and Reading assessments?
```{r}
mathRead<- global_ua2umgc1%>% tidyr::drop_na(49,236)
nrow (mathRead)
```
How many students per college took Math and Reading assessments?
```{r}
table(mathRead$college)
```

How many students took Math and Writing assessments?
```{r}
mathWrite<- global_ua2umgc1%>% tidyr::drop_na(49,39)
nrow (mathWrite)
```
How many students per college took Math and Writing assessments?
```{r}
table(mathWrite$college)
```

How many students took Reading and Writing assessments?
```{r}
readWrite<- global_ua2umgc1%>% tidyr::drop_na(236,39)
nrow (readWrite)
```
How many students per college took Reading and Writing assessments?
```{r}
table(readWrite$college)
```
To find out the numbers of students who took one assessment only:

```{r}
fourAttempts<- global_ua2umgc1[,c(1,41,2,42 ,230 ,25)]
fourAttempts[is.na(fourAttempts)] <- 0#replace missing values with zeros
singleAssessment <- subset(fourAttempts[(rowSums(fourAttempts[,c(3:6)])==1),])
colSums(singleAssessment[,c(3:6)])
aggregate(singleAssessment[,c(3:6)], list(singleAssessment$college), FUN=sum)
```
